### 2019-03-18 paper/main.tex
Starting the paper

\documentclass[acmtog]{acmart}

\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em 
b}\kern-.08emT\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}

\begin{document}

\title{Towards Detecting Stalkerware Through Network Traces}

\author{Audrey Randall}
\author{Hugh Feng}
\author{Yu-Wun Wang}
\affiliation{\institution{UCSD}}

\begin{abstract}
Spyware is known as unwanted software that sends user state and information to 
an external party. Often these apps are not inherently malicious to the 
operating system and are thus difficult to detect. We explore a subset of 
spyware that are available in the Android Play store intended for spying on 
another person though his or her cell phone and create a new method of 
identifying their presence through network signatures.  
\end{abstract}

\maketitle

\section{Introduction}
In a world where technology now pervades every aspect of our lives, some 
aspects of our relationships with intimate partners have changed too. 
Specifically, when these relationships become abusive, there are more options 
available to the abuser for attempting to retain control over their partner. 
One of these options is the ability to install monitoring software on their 
partner's phone or computer to record their online activity, communications, 
and location. We refer to such software as ``stalkerware.''  In a survey of 72 
domestic violence shelters performed by NPR in 2014, 85\% said they worked with 
survivors whose abusers had tracked their location using their smartphone's 
GPS. 75\% said they are working with clients who have had their conversations 
monitored by hidden stalkerware apps.\cite{shahani_smartphones}

Although stalkerware is superficially similar to other types of malware, a few 
key differences exist between them. First, stalkerware is meant to be installed 
deliberately, by someone with physical access to the device that is to be 
monitored. In the context of intimate partner abuse, this presents an enormous 
threat. An abuser will often know or be able to coerce passwords to the device 
from the victim, making traditional defense measures irrelevant. Second, the 
threat model used by malware developers includes sophisticated antivirus and 
intrusion detection systems (IDSs). Malware is therefore much more likely to 
attempt to obfuscate its network traffic. Third, stalkerware falls for the most 
part into two categories: apps that are explicitly advertised for surveilling 
spouses and partners, and apps that have a different stated use but can be 
repurposed to stalk a target. These are usually marketed for theft prevention, 
parental control of children, and employer control of employees. Previous 
literature refers to these as "dual-use" apps [5]. Determining how many users 
of a particular dual-use app are using it for intimate partner surveillance 
(IPS), and how many for its stated (usually legal) purpose, presents a 
significant challenge.

Therefore, we start by identifying a set of dual-use apps that appear to be 
marketed primarily for IPS. Apps that appear in Google searches for terms like 
"catch a cheating spouse," use vague language that appear to be marketed 
towards IPS, and label themselves as "spyware" became candidates that we 
considered. Such apps also differentiated themselves from more innocent apps by 
their price - they cost much more than a typical app, with monthly 
subscriptions ranging from \$12 to \$68 per month. We selected several of these 
to test. All of these apps brand themselves as spyware and advertise that their 
products are undetectable on the target phone, despite their disclaimers that 
they should not be used for any illegal activity. Some use language that 
appears designed to appeal to abusers. For example, underneath one promotional 
video, the app TheOneSpy has the disclaimer: "Note for this video: Don't 
confuse with the world "Loved Ones" as spouse or Girl friends! Word Loved ones 
has used for kids and teens." Many of these apps also refer to the tracked 
phone as the "target" phone, and advertise that once installed, the app is in 
"stealth mode," meaning completely undetectable.

The other category for stalkerware encompasses a large range of quality. Many 
apps advertised as stalkerware have absolutely no functionality other than 
advertisement of other apps. The few that are functional are often simplistic 
in both features and network patterns. Unlike dual-use apps, however, the vast 
majority are usually free with advertisements. These apps can be easily 
identified and found with a few keywords such as "spy","track", "locate", or 
"find".

\section{Related Work}
Previous studies [1,2], the media [3,4], and intimate partner violence (IPV) 
survivors have all reported that spyware is becoming an increasing source of 
intimate partner surveillance (IPS). Tracking functions supported by spyware 
allow stalkers to monitor communications, track locations, and remotely 
activate cameras and microphones [3,4]. In Dr. Ristenpart’s work [5], they 
proposed methods for searching IPS-related apps. By Google search query 
expansion and unsupervised classification, they collected 9,224 apps possibly 
related to IPS on Google play and open-web. They manually selected 70 apps for 
investigation. They observed the most fundamental functions of these apps are 
monitoring locations, communication logs and data, media contents, and phone 
usages. They also found that existing anti-spyware tools cannot effectively 
detect IPS-related apps.
Mobile apps are often identified via the User-Agent string of the HTTP request, 
when one is available [7]. With the increased use of HTTPS this may not always 
be the case, but we expect to find (based on conversations with authors of 
previous work) that security and best coding practices are not prioritized by 
stalkerware developers. Malware identification may be of limited use as well, 
since techniques are available to cluster malware that comes from the same 
source code into “families.” [8]

\section{Methodology}
\subsection{Finding Apps}
We selected thirty apps from a list provided by the team of Cornell researchers 
who performed the original large scale study of stalkerware[cite]. An 
additional fifteen apps were included as they were recently added to the app 
store. Apps were chosen for their diversity of purpose and the probability that 
they can be used as stalkerware. These apps are the most likely to be 
downloaded when a abuser without deep technical knowledge tries to install 
stalkerware.

We recognize that there are thousands of apps on the market that can be 
repurposed as stalkerware. Therefore, any useful process for identifying 
network signatures will eventually have to cover far more apps than we are 
starting out with. Our mere forty-five apps barely scratch the surface of the 
ecosystem, so they certainly do not provide a representative sample. Therefore, 
we did not employ any vigorous app selection methods, since we know this is 
just a starting point. Our hope is to eventually find a way to partially 
automate the signature identification process.

However, some characteristics of the stalkerware apps themselves may aid us in 
detecting them. For example, similar to malware, some groups of apps appear to 
be repackaged versions of each other. For example, PhoneSpector, 
HighsterMobile, AutoForward, EasySpy and Surepoint Spy all have separate 
websites, but the appearance of each of these sites is nearly identical. Upon 
closer inspection, although multiple companies are listed as the makers of the 
apps (Powerline Group Corp., ILF Mobile Apps, and PhoneSpector LLC), all have 
the same physical address listed. At least one blog that is supposedly run by 
an independent part reviewed apps that coincidentally were made by the same 
company [9]. Other app sites appear to be similar to each other in other ways, 
with many having a large panel with a darkened image background extolling the 
features of the app above two buttons, one for a “live demo” and the other to 
“buy now.” This is somewhat circumstantial evidence - it is entirely possible 
that these manufacturers simply chose similar web templates, or copy each 
other’s site in an attempt to undercut competition. However, if multiple groups 
of stalkerware apps are in fact made by only a few manufacturers, it may 
facilitate app identification. Similarities in network traces may indicate that 
the code used in the apps was made by the same developers.

\subsection{App Traffic}

Upon identifying the apps and locating them on the app store or app website, we 
proceeded to install the apps on two phones. One is a (what are our phones). 
After installing and confirming functionality, we began tracking the phone's 
network traffic using Wireshark. For the majority of the apps, a network trace 
of five to ten minutes is enough to detect traffic going to and from the 
stalkerware app as long as the app's tracked functions like text or GPS are 
altered or the tracker app or website has a manual update function. Those that 
do not have such functionality have all been fake stalkerware apps. The network 
captures themselves contain at least one packet that provides easy manual 
detection of the related app.

In addition to the above network captures, we also took twenty-four hours of 
network traffic of our own phones as a baseline for false positive rates. These 
captures also included periods of time that were deemed high risk for false 
positives as they emulated behaviour that is most likely to be caught by our 
signatures. Although this may not be enough to fully emulate an entire network, 
it is enough to prove the false positive rates on any given phone.

\section{Traffic Results}

The majority of stalkerware apps communicate though HTTP or HTTPS.

\section{temp}

Some examples.  A paginated journal article \cite{Abril07}, an enumerated 
journal article \cite{Cohen07}, a reference to an entire issue \cite{JCohen96}, 
a monograph (whole book) \cite{Kosiur01}, a monograph/whole book in a series 
(see 2a in spec. document)
\cite{Harel79}, a divisible-book such as an anthology or compilation 
\cite{Editor00} followed by the same example, however we only output the series 
if the volume number is given \cite{Editor00a} (so Editor00a's series should 
NOT be present since it has no vol. no.),
a chapter in a divisible book \cite{Spector90}, a chapter in a divisible book 
in a series \cite{Douglass98}, a multi-volume work as book \cite{Knuth97}, an 
article in a proceedings (of a conference, symposium, workshop for example) 
(paginated proceedings article) \cite{Andler79}, a proceedings article with all 
possible elements \cite{Smith10}, an example of an enumerated proceedings 
article \cite{VanGundy07}, an informally published work \cite{Harel78}, a 
doctoral dissertation \cite{Clarkson85}, a master's thesis: \cite{anisi03}, an 
online document / world wide web resource \cite{Thornburg01, Ablamowicz07, 
Poker06}, a video game (Case 1) \cite{Obama08} and (Case 2) \cite{Novak03} and 
\cite{Lee05} and (Case 3) a patent \cite{JoeScientist001}, work accepted for 
publication \cite{rous08}, 'YYYYb'-test for prolific author \cite{SaeediMEJ10} 
and \cite{SaeediJETC10}. Other cites might contain 'duplicate' DOI and URLs 
(some SIAM articles) \cite{Kirschmer:2010:AEI:1958016.1958018}. Boris / Barbara 
Beeton: multi-volume works as books \cite{MR781536} and \cite{MR781537}. A 
couple of citations with DOIs: 
\cite{2004:ITE:1009386.1010128,Kirschmer:2010:AEI:1958016.1958018}. Online 
citations: \cite{TUGInstmem, Thornburg01, CTANacmart}.

%
% The next two lines define the bibliography style to be used, and the 
%bibliography file.
\bibliographystyle{ACM-Reference-Format}
\bibliography{IPS_Measurement.bib}

% 
% If your work has an appendix, this is the place to put it.
\appendix

\section{Apps and Signatures}

\end{document}

### 2019-03-18 paper/main.tex
Update main.tex
fixed bib

@@
 We selected thirty apps from a list provided by the team of Cornell researchers 
-who performed the original large scale study of stalkerware[cite]. An 
+who performed the original large scale study of stalkerware\cite{chatterjee_spyware_2018}. An 
 additional fifteen apps were included as they were recently added to the app 
@@
 downloaded when a abuser without deep technical knowledge tries to install 
-stalkerware.
+stalkerware since they are either the first result upon searching for stalkerware, or are well known spyware apps due to advertisement or other reasons.
 
@@
 
-\section{temp}
-
-Some examples.  A paginated journal article \cite{Abril07}, an enumerated 
-journal article \cite{Cohen07}, a reference to an entire issue \cite{JCohen96}, 
-a monograph (whole book) \cite{Kosiur01}, a monograph/whole book in a series 
-(see 2a in spec. document)
-\cite{Harel79}, a divisible-book such as an anthology or compilation 
-\cite{Editor00} followed by the same example, however we only output the series 
-if the volume number is given \cite{Editor00a} (so Editor00a's series should 
-NOT be present since it has no vol. no.),
-a chapter in a divisible book \cite{Spector90}, a chapter in a divisible book 
-in a series \cite{Douglass98}, a multi-volume work as book \cite{Knuth97}, an 
-article in a proceedings (of a conference, symposium, workshop for example) 
-(paginated proceedings article) \cite{Andler79}, a proceedings article with all 
-possible elements \cite{Smith10}, an example of an enumerated proceedings 
-article \cite{VanGundy07}, an informally published work \cite{Harel78}, a 
-doctoral dissertation \cite{Clarkson85}, a master's thesis: \cite{anisi03}, an 
-online document / world wide web resource \cite{Thornburg01, Ablamowicz07, 
-Poker06}, a video game (Case 1) \cite{Obama08} and (Case 2) \cite{Novak03} and 
-\cite{Lee05} and (Case 3) a patent \cite{JoeScientist001}, work accepted for 
-publication \cite{rous08}, 'YYYYb'-test for prolific author \cite{SaeediMEJ10} 
-and \cite{SaeediJETC10}. Other cites might contain 'duplicate' DOI and URLs 
-(some SIAM articles) \cite{Kirschmer:2010:AEI:1958016.1958018}. Boris / Barbara 
-Beeton: multi-volume works as books \cite{MR781536} and \cite{MR781537}. A 
-couple of citations with DOIs: 
-\cite{2004:ITE:1009386.1010128,Kirschmer:2010:AEI:1958016.1958018}. Online 
-citations: \cite{TUGInstmem, Thornburg01, CTANacmart}.
-
 %
@@
 \bibliographystyle{ACM-Reference-Format}
-\bibliography{IPS_Measurement.bib}
+\bibliography{IPS_Measurement}
 

### 2019-03-18 paper/main.tex
Edited introduction

@@
 partner's phone or computer to record their online activity, communications, 
-and location. We refer to such software as ``stalkerware.''  In a survey of 72 
-domestic violence shelters performed by NPR in 2014, 85\% said they worked with 
-survivors whose abusers had tracked their location using their smartphone's 
-GPS. 75\% said they are working with clients who have had their conversations 
-monitored by hidden stalkerware apps.\cite{shahani_smartphones}
+and location. We refer to such software as ``stalkerware.''
 
-Although stalkerware is superficially similar to other types of malware, a few 
-key differences exist between them. First, stalkerware is meant to be installed 
+Although stalkerware is superficially similar to other types of malware, it has 
+a few key differences. First, stalkerware is meant to be installed 
 deliberately, by someone with physical access to the device that is to be 
@@
 parental control of children, and employer control of employees. Previous 
-literature refers to these as "dual-use" apps [5]. Determining how many users 
-of a particular dual-use app are using it for intimate partner surveillance 
-(IPS), and how many for its stated (usually legal) purpose, presents a 
-significant challenge.
+literature refers to these as "dual-use" apps\cite{chatterjee_spyware_2018}. 
+Some dual-use apps are ones that the survivor wants to keep installed, such as 
+``find my phone'' apps or social media apps that leak the user's location. The 
+most troubling example of this is Facebook, which most survivors want to keep 
+so that they can contact their support network for help.  
+Determining if a particular dual-use app is being used for 
+intimate partner surveillance (IPS) presents an enormous challenge. Given the 
+wide spectrum of apps that can be used to facilitate IPS and the limited scope 
+of this project, we chose to focus on more overt spyware.
 
-Therefore, we start by identifying a set of dual-use apps that appear to be 
-marketed primarily for IPS. Apps that appear in Google searches for terms like 
+Largely due to the differences between stalkerware and other malware, most 
+available information on the pervasiveness of stalkerware is anecdotal and 
+piecemeal. Small-scale studies on how widespread spyware is do exist, but they 
+have limitations. For example, in a survey of 72 
+domestic violence shelters performed by NPR in 2014, 85\% said they worked with 
+survivors whose abusers had tracked their location using their smartphone's 
+GPS. 75\% said they are working with clients who have had their conversations 
+monitored by hidden stalkerware apps.\cite{shahani_smartphones_nodate} However, 
+this study does not report how many individual clients experienced being 
+digitally stalked. Additionally, it and similar work relies on 
+reports from domestic violence shelters and health workers, which does not give 
+a complete picture of the situation. Little to no data exist regarding spyware 
+use on IPA victims who never visit a shelter. Traditionally, antivirus vendors 
+collect metrics about 
+malicious software, but antivirus often does not detect spyware 
+\cite{chatterjee_spyware_2018}. Alarmingly, the stalkerware 
+websites themselves claim to have hundreds of thousands of downloads per app, 
+but these numbers are not likely to be trustworthy. The goal of this work is 
+therefore to identify a means of identifying stalkerware in the wild so that it 
+can be enumerated. We collected the network signatures of 24 stalkerware apps 
+and showed that they could be easily distinguished from ordinary smartphone 
+network traffic. We also propose a simple method of generalizing our signatures 
+to spyware that we did not manually examine, and evaluate its robustness.
+
+We began by identifying a set of apps that appear to be 
+marketed primarily for IPS. We focused exclusively on Android apps, since our 
+two test phones were both Androids. Apps that appear in Google searches for 
+terms like 
 "catch a cheating spouse," use vague language that appear to be marketed 
 towards IPS, and label themselves as "spyware" became candidates that we 
-considered. Such apps also differentiated themselves from more innocent apps by 
-their price - they cost much more than a typical app, with monthly 
-subscriptions ranging from \$12 to \$68 per month. We selected several of these 
-to test. All of these apps brand themselves as spyware and advertise that their 
-products are undetectable on the target phone, despite their disclaimers that 
-they should not be used for any illegal activity. Some use language that 
-appears designed to appeal to abusers. For example, underneath one promotional 
-video, the app TheOneSpy has the disclaimer: "Note for this video: Don't 
-confuse with the world "Loved Ones" as spouse or Girl friends! Word Loved ones 
-has used for kids and teens." Many of these apps also refer to the tracked 
-phone as the "target" phone, and advertise that once installed, the app is in 
-"stealth mode," meaning completely undetectable.
+considered. Overt spyware is not generally available from the app store - it 
+must be downloaded from the manufacturer sites. It also costs much more than a 
+typical app, with monthly 
+subscriptions ranging from \$12 to \$70 per month. The exception is an app that 
+we call SpyToMobile, which survives on the app store by frequently 
+``reskinning'' itself (see section \ref{reskinning}).  
+We selected several of these to test. All of these apps brand themselves as 
+spyware and advertise that their products are undetectable on the target phone, 
+despite also having disclaimers in small text that their software should not be 
+used for any illegal activity. Some use language that appears designed to 
+appeal to abusers. For example, underneath one promotional 
+video, the app TheOneSpy has the disclaimer: ``Note for this video: Don't 
+confuse with the world `Loved Ones' as spouse or Girl friends! Word Loved ones 
+has used for kids and teens.'' Many of these apps also refer to the tracked 
+phone as the ``target'' phone, and advertise that once installed, the app is in 
+``stealth mode,'' meaning completely undetectable. None of these required 
+rooting the phone. When installed, they ask for all the permissions they 
+require, including device administrator privileges. They are capable of 
+blocking incoming calls, recording messages that have been deleted, recording 
+the screen of the phone using accessibility features, monitoring apps such as 
+Facebook, WhatsApp, Kik, and Viber, and more.
+
+Other apps were overt spyware, but nevertheless available from the Play Store. 
+They fell into two categories: spyware that reskinned itself to appear to be 
+many different apps, and apps designed for parents to keep track of children 
+(or in one case, for adult children to track elderly parents.) For the most 
+part, this latter category was offered by antivirus companies such as Avast and 
+Norton. These apps offered 
+multiple features, such as call screening, blocking Google search results, 
+recording text messages and call logs, and ``panic buttons'' that would allow 
+the surveilled phone to contact the surveillant and raise an alarm. They do not 
+hide their app icons and generally make an effort to notify the user that the 
+monitoring app is installed on their phone. The spyware that did not notify 
+users of its presence mostly consisted of one app, called SpyToMobile, that was 
+provided on the Play Store under many different names.
+
+We also identified many apps that were designed to track location or text 
+messages, but were less comprehensive than the overt, off-store spyware. They 
+track one feature each instead of tracking location, communication, and 
+browsing history all at once. For the most part, these apps were free and 
+available on the Google Play Store. Most of these were designed to keep track 
+of the locations of the users' friends.
+
+\section{The Stalkerware Ecosystem}
+\subsection{The Practice of ``Reskinning''}
+\label{reskinning}
+
+Somewhere: put a note about the weird thing where the paid apps try to make you 
+download stuff again. Maybe it's just us? Maybe they're trying to boost 
+download count?
+
+Some spyware has a notification that the app is running, but that can be 
+disabled. Those ones don't hide their icon, but you might have to go to All 
+Apps to find it.
+
+\subsection{App Quality}
 
@@
 advertisement of other apps. The few that are functional are often simplistic 
-in both features and network patterns. Unlike dual-use apps, however, the vast 
+in both features and network patterns. Unlike the overt apps, however, the vast 
 majority are usually free with advertisements. These apps can be easily 
@@
 We selected thirty apps from a list provided by the team of Cornell researchers 
-who performed the original large scale study of stalkerware\cite{chatterjee_spyware_2018}. An 
+who performed the original large scale study of stalkerware[cite]. An 
 additional fifteen apps were included as they were recently added to the app 
@@
 downloaded when a abuser without deep technical knowledge tries to install 
-stalkerware since they are either the first result upon searching for stalkerware, or are well known spyware apps due to advertisement or other reasons.
+stalkerware.
 
@@
 
-%
-% The next two lines define the bibliography style to be used, and the 
-%bibliography file.
+\section{Future Work}
+
+Make machine learning identify stalkerware on the app store, download it, 
+profile it. Then train more ML to pick out the malicious signatures? Would that 
+even work? What would it learn that we can't?
+
+\section{Conclusion}
+
 \bibliographystyle{ACM-Reference-Format}
@@
 
-% 
-% If your work has an appendix, this is the place to put it.
 \appendix

### 2019-03-18 paper/main.tex

@@
 We selected thirty apps from a list provided by the team of Cornell researchers 
-who performed the original large scale study of stalkerware[cite]. An 
+who performed the original large scale study of 
+stalkerware\cite{chatterjee_spyware_2018}. An 
 additional fifteen apps were included as they were recently added to the app 
@@
 downloaded when a abuser without deep technical knowledge tries to install 
-stalkerware.
+stalkerware since they are either the first result upon searching for 
+stalkerware, or are well known spyware apps due to advertisement or other 
+reasons.
 

### 2019-03-18 paper/main.tex
merging with introduction

--- 2019-03-18 paper/main.tex
@@
 an independent part reviewed apps that coincidentally were made by the same 
-company [9]. Other app sites appear to be similar to each other in other ways, 
+company\cite{noauthor_best_nodate}. Other app sites appear to be similar to each other in other ways, 
 with many having a large panel with a darkened image background extolling the 
-features of the app above two buttons, one for a “live demo” and the other to 
-“buy now.” This is somewhat circumstantial evidence - it is entirely possible 
-that these manufacturers simply chose similar web templates, or copy each 
-other’s site in an attempt to undercut competition. However, if multiple groups 
+features of the app above two buttons, one for a "live demo" and the other to 
+"buy now." This is somewhat circumstantial evidence - it is entirely possible 
+that these manufacturers simply chose similar web templates, or copied each 
+other's site in an attempt to undercut competition. However, if multiple groups 
 of stalkerware apps are in fact made by only a few manufacturers, it may 
-facilitate app identification. Similarities in network traces may indicate that 
-the code used in the apps was made by the same developers.
+facilitate app identification.
+
+After our investigation on these apps, we can confirm that, at least from the few that we have selected, many stalkerware apps are related in some fashion to each other.
+The most notable being the group of apps stated above, and a single app called spy2mobile.
+Spy2mobile is an interesting case because it fits the description of a generic stalkerware app so closely that it is the perfect example of spyware on the Play Store.
+Moreover, this single app has been repackaged multiple times.
+We have discovered that there are at least 6 copies of the app on the Play store, all with different developers and different names.
+While this is still circumstantial evidence that most stalkerware often contains copies of each other, we can at least conclue that our forty-five apps constitute a larger percentage than anticipated.
 
@@
 
+What causes most stalkerware to send packets?
+Our captures and testing show that there are three main categories of updating tracker state: manual, timed, and on tracked feature.
+Most free apps fall into the manual update method, where there is a button on a website or on a phone app that will send a signal packet to the stalkerware app that initalizes the upload.
+Most paid apps also include a timed auto-update feature, where an update will be sent every few minutes.
+A very small subset of both advertised that it receives a "real time notification" every time email, texts, calls, or GPS, was changed or added to.
+Our results show that none of the stalkerware apps were able to send in real time.
+
 In addition to the above network captures, we also took twenty-four hours of 
@@
 it is enough to prove the false positive rates on any given phone.
+
+\subsection{Network Signatures}
 

### 2019-03-18 paper/main.tex
edit traffic result

--- 2019-03-18 paper/main.tex
@@
 an independent part reviewed apps that coincidentally were made by the same 
-company\cite{noauthor_best_nodate}. Other app sites appear to be similar to each other in other ways, 
+company [9]. Other app sites appear to be similar to each other in other ways, 
 with many having a large panel with a darkened image background extolling the 
-features of the app above two buttons, one for a "live demo" and the other to 
-"buy now." This is somewhat circumstantial evidence - it is entirely possible 
-that these manufacturers simply chose similar web templates, or copied each 
-other's site in an attempt to undercut competition. However, if multiple groups 
+features of the app above two buttons, one for a “live demo” and the other to 
+“buy now.” This is somewhat circumstantial evidence - it is entirely possible 
+that these manufacturers simply chose similar web templates, or copy each 
+other’s site in an attempt to undercut competition. However, if multiple groups 
 of stalkerware apps are in fact made by only a few manufacturers, it may 
-facilitate app identification.
-
-After our investigation on these apps, we can confirm that, at least from the few that we have selected, many stalkerware apps are related in some fashion to each other.
-The most notable being the group of apps stated above, and a single app called spy2mobile.
-Spy2mobile is an interesting case because it fits the description of a generic stalkerware app so closely that it is the perfect example of spyware on the Play Store.
-Moreover, this single app has been repackaged multiple times.
-We have discovered that there are at least 6 copies of the app on the Play store, all with different developers and different names.
-While this is still circumstantial evidence that most stalkerware often contains copies of each other, we can at least conclue that our forty-five apps constitute a larger percentage than anticipated.
+facilitate app identification. Similarities in network traces may indicate that 
+the code used in the apps was made by the same developers.
 
@@
 
-What causes most stalkerware to send packets?
-Our captures and testing show that there are three main categories of updating tracker state: manual, timed, and on tracked feature.
-Most free apps fall into the manual update method, where there is a button on a website or on a phone app that will send a signal packet to the stalkerware app that initalizes the upload.
-Most paid apps also include a timed auto-update feature, where an update will be sent every few minutes.
-A very small subset of both advertised that it receives a "real time notification" every time email, texts, calls, or GPS, was changed or added to.
-Our results show that none of the stalkerware apps were able to send in real time.
-
 In addition to the above network captures, we also took twenty-four hours of 
@@
 
-\subsection{Network Signatures}
-
 \section{Traffic Results}
 
-The majority of stalkerware apps communicate though HTTP or HTTPS.
+The majority of stalkerware apps communicate though HTTP or HTTPS, while some use their own protocols.
+We examined the domain, SNI, User-Agent, and HTTP host, for each app.
+The words “spy,” “find,” and “track” appeared frequently in various fields of the traffic.
+The most common place to find them was in the destination domain, which we found using Wireshark’s reverse DNS lookup tool.
+12 of the 26 apps that we eventually found signatures for contained these spyware keywords in their domains.
+We identified the following generalized signatures that can be used to identify most of our apps given nothing but information available on the Google Play store.
 

### 2019-03-18 paper/main.tex

--- 2019-03-18 paper/main.tex
@@
 
-The majority of stalkerware apps communicate though HTTP or HTTPS.
+The majority of stalkerware apps communicate though HTTP or HTTPS, while some use their own protocols.
+We examined the domain, SNI, User-Agent, and HTTP host, for each app.
+The words “spy,” “find,” and “track” appeared frequently in various fields of the traffic.
+The most common place to find them was in the destination domain, which we found using Wireshark’s reverse DNS lookup tool.
+12 of the 26 apps that we eventually found signatures for contained these spyware keywords in their domains.
+We identified the following generalized signatures that can be used to identify most of our apps given nothing but information available on the Google Play store.
 

### 2019-03-18 paper/main.tex
Update main.tex
Almost done with method

--- 2019-03-18 paper/main.tex
@@
 After our investigation on these apps, we can confirm that, at least from the few that we have selected, many stalkerware apps are related in some fashion to each other.
-The most notable being the group of apps stated above, and a single app called spy2mobile.
-Spy2mobile is an interesting case because it fits the description of a generic stalkerware app so closely that it is the perfect example of spyware on the Play Store.
+The most notable being the group of apps stated above, and a single app mentioned before called SpyTomobile.
+SpyTomobile is an interesting case because it fits the description of a generic stalkerware app so closely that it is the perfect example of spyware on the Play Store.
 Moreover, this single app has been repackaged multiple times.
 We have discovered that there are at least 6 copies of the app on the Play store, all with different developers and different names.
-While this is still circumstantial evidence that most stalkerware often contains copies of each other, we can at least conclue that our forty-five apps constitute a larger percentage than anticipated.
+While this is still circumstantial evidence that most stalkerware often contains copies of each other, we can at least conclude that our forty-five apps constitute a larger percentage than anticipated.
 
@@
 A very small subset of both advertised that it receives a "real time notification" every time email, texts, calls, or GPS, was changed or added to.
-Our results show that none of the stalkerware apps were able to send in real time.
+Our results show that none of the stalkerware apps were able to send in real time, all the apps advertised as real time simply updated at a more frequent frequency than other apps.
 
@@
 
+When the network traffic is captured and the suspicious packets are identified, the next step would be to form a Network signature that can filter out those packets.
+But what can we use that isolates stalkerware traffic from normal traffic?
+To begin with, we must look at the packet identifiers that allow us to find the suspicious packets.
+\begin{itemize}
+	\item Application Layer
+	\begin{itemize}
+		\item HTTP
+		\begin{itemize}
+			\item packet content
+			\item User agent
+		\end{itemize}
+		\item HTTP and HTTPS headers
+		\item Packet length
+		\item Domain Name
+		\item Host Name
+		\item Location Requests
+	\end{itemize}
+	\item Transport Layer
+	\begin{itemize}
+		\item TLS 1.2
+		\begin{itemize}
+			\item Server Name Indication
+		\end{itemize}
+		\item TCP
+		\begin{itemize}
+			\item Ports
+			\item Sequence number
+		\end{itemize}
+	\end{itemize}
+	\item Internet Layer
+	\begin{itemize}
+		\item IP address
+		\item IP version
+	\end{itemize}
+	\item Other
+	\begin{itemize}
+		\item Packet frequency
+	\end{itemize}
+\end{itemize}
+
+All of the above signatures are able to be filtered out through a Wireshark filter or made into a rule for a Network Intrusion Detection System such as Snort.
+There are many other parts of the packets that we could attempt to match signatures for, we will explain why we cannot add more to this list.
 \section{Traffic Results}

### 2019-03-18 paper/main.tex
Update main.tex
The table

@@
 
+\usepackage{makecell}
+\renewcommand\cellalign{tl}
 \def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em 
@@
 \section{Apps and Signatures}
+\begin{table*}
+\begin{tabular}{p{5cm}p{5cm}p{5cm}}
+	\toprule
+	App & Signature & Relevant Info \\
+	\midrule
+	HelloSpy & \makecell{HTTP Post to\\ <numbers>.dedicated.codero.net} & Same as TheTruthSpy HTTP \\
 
+	TheTruthSpy & \makecell{HTTP Post to\\ <numbers>.dedicated.codero.net\\ User agent has hellospy in it} & Same as HelloSpy HTTP \\
+
+	SpyMyFone & \makecell{HTTP 101 Switching Protocols response\\
+	Domain: data-api.spymyfone.com\\SNI my.spymyfone.com.\\
+	Domain: ws.spyzie.com\\SNI ws.spyzie.com\\
+	Domains: app-api.phonedata.me\\ws.phonedata.me\\
+	SNI with unknown domain:\\ app-api.phonedata.me} & Uses WebSocket protocol and HTTP with User agent=aliyun-sdk-android/2.3.0/Dalvik/2.1.0 (Linux; U; Android 7.1.2; Nexus 5X Build/NJH47B \\
+
+	Spyzie & \makecell{The same as SpyMyFone.\\ We are sure that SpyMyPhone\\ talks to spyzie.com} & Same as SpyMyFone \\
+
+	iSpyoo & probably same signatures as HelloSpy and TheTruthSpy given identical websites, but apk is broken & Nonfunctional \\
+
+	mSpy & \makecell{POST to pipe.thd.cc\\
+	PUT to a18.dav.mspyonline.com\\
+	Domain: apiv4.alter757.info} & HTTPS \\
+
+	SMS Tracker (TheHar) & \makecell{Domain:uploads.spy2mobile.com\\ Domain contains sap4mobile} & spytomobile group (does NOT use HTTPS) \\
+
+	SMS Tracker TM & \makecell{Domain:cust-198-154-111-218.\\corexchange.com \\ SNI:messages02.smstracker.com} & Only tracks text. HTTPS \\
+
+	Find My Friends & Domain:production-finderapps-lb-1188906093.us-east-1.elb.amazonaws.com & HTTPS\\
+
+	Avast Anti-Theft & domain:Antitheft.ns1.ff.avast.com& HTTPS. High packet counts\\
+
+	Family Locator by ZoeMob & SNIs: celulocen.zendesk.com, api.familysafetyproduction.com
+	Domains: proxy.vip.pod5.iad1.zdsys.com, www.zoemob.com & same as Life360
+	HTTPS \\
+
+	Couple Tracker -Mobile monitor & 162-144-96-67.unifiedlayer.com & HTTPS \\
+
+	Call and Message Tracker -Remote karanth & \makecell{SNI=www.callsmstracker.com
+	\\Domain contains onlinehome-server.com} & Similar to Cell Tracker, but uses HTTPS instead of HTTP \\
+
+	Mobile Surveillance and Security
+	by Trackview & \makecell{HTTP req:\\ "GET /create\_session HTTP/1.1"\\ User agent:test \\Host:relay.google.com\\
+	Domains: relay.l.google.com,\\ stun.l.google.com} & Uses STUN protocol \\
+
+\end{tabular}
+\end{table*}
+
+\begin{table*}
+\begin{tabular}{p{5cm}p{5cm}p{5cm}}
+	\toprule
+	App & Signature & Relevant Info \\
+	\midrule
+	Norton Family parental control & \makecell{domain: spoc-muw1.norton.com,\\spoc-mue1.norton.com\\
+	User-Agent: NOF/4.9.2.12/Android/8.1.0\\
+	SNI: family.norton.com} & HTTP POST with protobufs, or TLS. \\
+
+	Senior Safety App & \makecell{POST to \\97.logger.mobi/signalr\_v1/<stuff>\\
+	97.logger.mobi/auth/token} & requires payment\\
+
+	Invisible Mobile GPS Tracker by
+	GPSWOX.COM & \makecell{SNI:dn.gpswox.com\\ Domain:gpswox.\\llcspnavigatio.netdna-cdn.com} & HTTPS \\
+
+	Family GPS Locator by GeoZilla & \makecell{Domain=static.<some-ip>.\\clients.your-server.de\\
+	SNI contains geozilla w/ aws domains} & NOT HTTPS (wrong ports), but TLS \\
+
+	Phone Tracker By Number/Phone Tracker Family Locator & http://66.147.232.135:8080/signalr & HTTP \\
+
+	Automatic Call Recorder & \makecell{Domain: http://winner-lb2-\\f918b4c7bf5ab40c.\\elb.us-east-1.amazonaws.com/ }& HTTPS \\
+
+	Find my Kids: Child GPS-watch and phone tracker & server name api.findmykids.org & Talks to yandex.net? Russian something. 
+	HTTPS \\
+
+	Live Mobile Number Tracker & \makecell{GET with host=clk.trkmobi.net\\
+	SNI track.56txs4.com, no domain\\
+	Domain cs156.adn.rhocdn.net\\ with SNI req..startappservice.com,\\
+	domain cs1112.wpc.rhocdn.net\\ with SNI info.startappservice.com} & No actual tracking functions. Sets your location to Fawn creek, KS \\
+
+	track my phone pro & Domain:trackmyphones.com & HTTPS from the website, HTTP over TLS from the app \\
+
+	Cell Phone Tracker & Domain:spy2mobile.com & SpyToMobile lookalike \\
+
+	Cell Tracker - Trackme & Domain:Onlinehome-server.com
+	SNI:www.callsmstracker.com & Similar to Call and Message tracker. Sends a post to a separate service. \\
+
+	Texting, Chat, Phone Spy by Maxlo & Domain:spy2mobile.com & SpyToMobile lookalike \\
+\end{tabular}
+
+\end{table*}
 \end{document}

### 2019-03-19 paper/main.tex
edit traffic result

@@
 
+\begin{table*}
+\begin{tabular}{p{5cm}p{5cm}p{5cm}}
+	\toprule
+	Generalized Signature & Unique Apps & Total Apps \\
+	Domain contains “spy,” “track,” “find” & 6 & 12 \\
+	SNI contains “spy,” “track,” “find” & 6 & 6 \\
+	User-Agent contains “spy,” “track,” “find” & 1 & 3 \\
+	User-Agent contains known app name & 1 & 1 \\
+	Domain contains known app name & 3 & 4 \\
+	SNI contains known app name & 1 & 1 \\
+	SNI contains known app manufacturer & 3 & 3 \\
+	Domain contains known app manufacturer & 3 & 3 \\
+	\midrule
+\end{tabular}
+\end{table*}
+
+\section{Reskinned Applications}
+
 \section{Future Work}

### 2019-03-19 paper/main.tex
Added to methodology, rearranged some things

--- 2019-03-18 paper/main.tex
@@
 the same physical address listed. At least one blog that is supposedly run by 
-an independent part reviewed apps that coincidentally were made by the same 
-company\cite{noauthor_best_nodate}. Other app sites appear to be similar to each other in other ways, 
+an independent party reviewed apps that coincidentally were all made by the 
+same company\cite{noauthor_best_nodate}. Other app sites appear to be similar 
+to each other in other ways, 
 with many having a large panel with a darkened image background extolling the 
@@
 that these manufacturers simply chose similar web templates, or copied each 
-other's site in an attempt to undercut competition. However, if multiple groups 
-of stalkerware apps are in fact made by only a few manufacturers, it may 
-facilitate app identification.
+other's site in an attempt to undercut competition. We therefore confirmed our 
+suspicions by checking if the traffic signatures were also similar. In multiple 
+cases, this was true (see section \ref{app_families}). App identification may 
+be easier to scale since multiple groups of stalkerware apps are in fact made 
+by only a few manufacturers.
 
-After our investigation on these apps, we can confirm that, at least from the few that we have selected, many stalkerware apps are related in some fashion to each other.
-The most notable being the group of apps stated above, and a single app mentioned before called SpyTomobile.
-SpyTomobile is an interesting case because it fits the description of a generic stalkerware app so closely that it is the perfect example of spyware on the Play Store.
-Moreover, this single app has been repackaged multiple times.
-We have discovered that there are at least 6 copies of the app on the Play store, all with different developers and different names.
-While this is still circumstantial evidence that most stalkerware often contains copies of each other, we can at least conclude that our forty-five apps constitute a larger percentage than anticipated.
+\subsection{Experimental Setup}
+Out of the 45 apps we originally selected from Dr. Ristenpart's ML-curated list 
+of stalkerware, 36 still existed on the app store. We installed these one at a 
+time on one or both of two test phones, a Nexus 5X and a Nexus 6P.These models 
+were chosen simply because they were readily available. Stalkerware user 
+models  fall into two types: either an app is installed on the target phone and 
+a login to a web portal is provided for the attacker to view the results, or 
+the app comes with an ``attacker'' app and a ``target'' app, and the attacker 
+app must be installed on another phone.
 
-\subsection{App Traffic}
-
-Upon identifying the apps and locating them on the app store or app website, we 
-proceeded to install the apps on two phones. One is a (what are our phones). 
-After installing and confirming functionality, we began tracking the phone's 
-network traffic using Wireshark. For the majority of the apps, a network trace 
+After installing an app, we first confirmed that it was functional and capable 
+of acting like stalkerware. 
+We then began tracking the phone's network traffic using Wireshark. For the 
+majority of the apps, a network trace 
 of five to ten minutes is enough to detect traffic going to and from the 
@@
 
-What causes most stalkerware to send packets?
-Our captures and testing show that there are three main categories of updating tracker state: manual, timed, and on tracked feature.
-Most free apps fall into the manual update method, where there is a button on a website or on a phone app that will send a signal packet to the stalkerware app that initalizes the upload.
-Most paid apps also include a timed auto-update feature, where an update will be sent every few minutes.
-A very small subset of both advertised that it receives a "real time notification" every time email, texts, calls, or GPS, was changed or added to.
-Our results show that none of the stalkerware apps were able to send in real time, all the apps advertised as real time simply updated at a more frequent frequency than other apps.
+\subsection{Ethical Considerations}
+
+We created two aliases in order to avoid exposing any personal information to 
+an ecosystem that is notorious for mishandling it\cite{ristenpart_ucsd_talk}. 
+It is likely that the privacy of victims is 
+not a high priority for anyone prepared to monetize abusive relationships, and 
+stalkerware manufacturers have leaked victims' information in the past 
+\cite{koebler_stalkerware_2018}. We took precautions by deleting all personal 
+data that had been on the phones at the start of the project. However, we were 
+not quite cautious enough - the app SpyMyFone managed to scrape a list of 
+deleted contacts off of the Nexus 5X. As of this moment, we do not know how. We 
+have deleted the account and requested that SpyMyFone delete all information 
+associated with it from their records, but we have no evidence that they have 
+complied. This served as a valuable and sobering lesson for the future.
+
+The original goal of this project was to identify traffic signatures so that 
+they could be detected by an IDS (Intrusion Detection System) or a network 
+tap in an anonymized fashion. We hoped to use differential privacy techniques 
+such as Google's RAPPOR algorithm \cite{erlingsson_rappor:_2014} to collect 
+aggregated statistics about stalkerware use, without giving ourselves the 
+ability to identify any particular device that had stalkerware installed. Upon 
+further investigation before we began the project, this turned out to be 
+insufficient protection. We as a computer 
+scientists do not have the expertise required to assist victims of abusive 
+relationships or domestic violence. We chose not to take our research in this 
+direction to avoid causing any unintended harm. We limit ourselves to 
+identifying traffic signatures on apps that we installed on personal phones.
+
+Wiretapping the phones was accomplished by setting up our personal computers as 
+WiFi hotspots. Since we controlled the passwords required to connect to our 
+networks, and Windows alerts the user when a device connects to its mobile 
+hotspot, we were able to ensure that we did not tap any traffic other than that 
+of the test phones.
+
+\subsection{App Traffic}
+
+What causes most stalkerware to send packets? Our captures and testing show 
+that there are three main categories of updating tracker state: manual, timed, 
+and on tracked feature. Most free apps fall into the manual update method, 
+where there is a button on a website or on a phone app that will send a signal 
+packet to the stalkerware app that initializes the upload. Most paid apps also 
+include a timed auto-update feature, where an update will be sent every few 
+minutes. A very small subset of both advertised that it receives a "real time 
+notification" every time email, texts, calls, or GPS, was changed or added to. 
+Our results show that none of the stalkerware apps were able to send in real 
+time, all the apps advertised as real time simply updated at a more frequent 
+frequency than other apps.
 
@@
 
-The majority of stalkerware apps communicate though HTTP or HTTPS, while some use their own protocols.
-We examined the domain, SNI, User-Agent, and HTTP host, for each app.
-The words “spy,” “find,” and “track” appeared frequently in various fields of the traffic.
-The most common place to find them was in the destination domain, which we found using Wireshark’s reverse DNS lookup tool.
-12 of the 26 apps that we eventually found signatures for contained these spyware keywords in their domains.
-We identified the following generalized signatures that can be used to identify most of our apps given nothing but information available on the Google Play store.
+The majority of stalkerware apps communicate though HTTP or HTTPS, while some 
+use their own protocols. We examined the domain, SNI, User-Agent, and HTTP 
+host, for each app. The words “spy,” “find,” and “track” appeared frequently in 
+various fields of the traffic. The most common place to find them was in the 
+destination domain, which we found using Wireshark’s reverse DNS lookup tool. 
+12 of the 26 apps that we eventually found signatures for contained these 
+spyware keywords in their domains. We identified the following generalized 
+signatures that can be used to identify most of our apps given nothing but 
+information available on the Google Play store.
+
+\subsection{App ``Families''}
+\label{app_families}
+After our investigation on these apps, we can confirm that, at least from the 
+few that we have selected, many stalkerware apps are related in some fashion to 
+each other. The most notable being the group of apps stated above, and a single 
+app mentioned before called SpyTomobile. SpyTomobile is an interesting case 
+because it fits the description of a generic stalkerware app so closely that it 
+is the perfect example of spyware on the Play Store. Moreover, this single app 
+has been repackaged multiple times. We have discovered that there are at least 
+6 copies of the app on the Play store, all with different developers and 
+different names. While this is still circumstantial evidence that most 
+stalkerware often contains copies of each other, we can at least conclude that 
+our forty-five apps constitute a larger percentage than anticipated.
+
+PUT NOTE HERE ABOUT THE FAMILIES THAT WE DID NOT CONFIRM VIA TRAFFIC, BUT 
+INSTEAD VIA LOOKING AT THE WEBSITES!! Otherwise we're fabricating results.
+
+\begin{table*}
+\begin{tabular}{p{5cm}p{5cm}p{5cm}}
+	\toprule
+	Generalized Signature & Unique Apps & Total Apps \\
+	\hline
+	Domain contains “spy,” “track,” “find” & 6 & 12 \\
+	SNI contains “spy,” “track,” “find” & 6 & 6 \\
+	User-Agent contains “spy,” “track,” “find” & 1 & 3 \\
+	User-Agent contains known app name & 1 & 1 \\
+	Domain contains known app name & 3 & 4 \\
+	SNI contains known app name & 1 & 1 \\
+	SNI contains known app manufacturer & 3 & 3 \\
+	Domain contains known app manufacturer & 3 & 3 \\
+	\midrule
+\end{tabular}
+\end{table*}
 

### 2019-03-19 paper/main.tex
Introduction and future work

@@
 
-Although stalkerware is superficially similar to other types of malware, it has 
-a few key differences. First, stalkerware is meant to be installed 
+Stalkerware is not as widely studied as other types of malware, and much less 
+information is available regarding it. Although it is superficially 
+similar to other types of malware, there exist a few key differences. First, 
+stalkerware is meant to be installed 
 deliberately, by someone with physical access to the device that is to be 
@@
 threat. An abuser will often know or be able to coerce passwords to the device 
-from the victim, making traditional defense measures irrelevant. Second, the 
+from the victim, making traditional defense measures irrelevant. This is one 
+example of how traditional assumptions about security often do not apply in the 
+context of IPV (intimate partner violence). Second, the 
 threat model used by malware developers includes sophisticated antivirus and 
-intrusion detection systems (IDSs). Malware is therefore much more likely to 
-attempt to obfuscate its network traffic. Third, stalkerware falls for the most 
-part into two categories: apps that are explicitly advertised for surveilling 
-spouses and partners, and apps that have a different stated use but can be 
-repurposed to stalk a target. These are usually marketed for theft prevention, 
-parental control of children, and employer control of employees. Previous 
-literature refers to these as "dual-use" apps\cite{chatterjee_spyware_2018}. 
-Some dual-use apps are ones that the survivor wants to keep installed, such as 
+intrusion detection systems (IDSs). Both malware and stalkerware need to hide 
+their presence on the target device, but malware is much more likely to 
+attempt to obfuscate its network traffic. Stalkerware does not: it does not 
+need to. Most antivirus does not detect apps capable of monitoring a target as 
+potentially dangerous \cite{chatterjee_spyware_2018}. This presents an 
+opportunity to glean information about stalkerware that is not available in the 
+study of other forms of malware. Third, stalkerware falls 
+for the most part into two categories: apps that are explicitly advertised for 
+surveilling spouses and partners, and apps that have a different stated use but 
+can be repurposed to stalk a target. These are usually marketed for theft 
+prevention, finding lost devices, parental control of children, and employer 
+control of employees. Previous literature refers to these as "dual-use" 
+apps\cite{chatterjee_spyware_2018}. Some dual-use apps are ones that the 
+victim wants to keep installed, such as 
 ``find my phone'' apps or social media apps that leak the user's location. The 
-most troubling example of this is Facebook, which most survivors want to keep 
-so that they can contact their support network for help.  
-Determining if a particular dual-use app is being used for 
-intimate partner surveillance (IPS) presents an enormous challenge. Given the 
-wide spectrum of apps that can be used to facilitate IPS and the limited scope 
-of this project, we chose to focus on more overt spyware.
+most troubling example of this is Facebook, which most victims want to keep 
+so that they can contact their support network for help.  Determining if a 
+particular dual-use app is being used for intimate partner surveillance (IPS) 
+presents an enormous challenge. Given the wide spectrum of apps that can be 
+used to facilitate IPS and the limited scope of this project, we chose to focus 
+on more overt spyware.
 
 Largely due to the differences between stalkerware and other malware, most 
-available information on the pervasiveness of stalkerware is anecdotal and 
-piecemeal. Small-scale studies on how widespread spyware is do exist, but they 
-have limitations. For example, in a survey of 72 
+available information on the \textit{pervasiveness} of stalkerware is anecdotal 
+and piecemeal. Small-scale studies on how widespread spyware is do exist, but 
+they have limitations. For example, in a survey of 72 
 domestic violence shelters performed by NPR in 2014, 85\% said they worked with 
 survivors whose abusers had tracked their location using their smartphone's 
-GPS. 75\% said they are working with clients who have had their conversations 
+GPS. 75\% said they have worked with clients who have had their conversations 
 monitored by hidden stalkerware apps.\cite{shahani_smartphones_nodate} However, 
@@
 digitally stalked. Additionally, it and similar work relies on 
-reports from domestic violence shelters and health workers, which does not give 
+reports from domestic violence shelters and health workers, which do not give 
 a complete picture of the situation. Little to no data exist regarding spyware 
-use on IPA victims who never visit a shelter. Traditionally, antivirus vendors 
+use on IPV victims who never visit a shelter. Traditionally, antivirus vendors 
 collect metrics about 
@@
 therefore to identify a means of identifying stalkerware in the wild so that it 
-can be enumerated. We collected the network signatures of 24 stalkerware apps 
-and showed that they could be easily distinguished from ordinary smartphone 
+can be enumerated. We identified unique signatures in the traffic of 24 
+stalkerware apps, by examining a traffic features such as domain names, HTTP 
+header fields, protocol, and server name indicators (SNIs). For a complete 
+list, see section \ref{network_signatures}. These signatures can be used by 
+antivirus software and IDSs to determine how widespread stalkerware is. We show 
+that these signatures are distinguishable from ordinary smartphone 
 network traffic. We also propose a simple method of generalizing our signatures 
@@
 of the test phones. 
+\section{Results}
+
+\subsection{Generalizing Signatures}
+
+We picked our three keywords because of xyz reasons outlined in the checkpoint
+
+\begin{table*}
+	\begin{tabular}{p{5cm}p{5cm}p{5cm}}
+		\toprule
+		Generalized Signature & Unique Apps & Total Apps \\
+		\hline
+		Domain contains “spy,” “track,” “find” & 6 & 12 \\
+		SNI contains “spy,” “track,” “find” & 6 & 6 \\
+		User-Agent contains “spy,” “track,” “find” & 1 & 3 \\
+		User-Agent contains known app name & 1 & 1 \\
+		Domain contains known app name & 3 & 4 \\
+		SNI contains known app name & 1 & 1 \\
+		SNI contains known app manufacturer & 3 & 3 \\
+		Domain contains known app manufacturer & 3 & 3 \\
+		\midrule
+	\end{tabular}
+\end{table*}
+
+In the subset of apps we studied, the words “spy,” “find,” and “track” appeared 
+frequently in various fields of the traffic. The most common place to find them 
+was in the destination domain, which we found using Wireshark’s reverse DNS 
+lookup tool. 12 of the 26 apps that we eventually found signatures for 
+contained these spyware keywords in their domains. 
+For the apps whose traffic doesn’t contain “spy,” “find,” or “track,” we will 
+next check for the app name and manufacturer name or substrings of these two. 
+Using these indicators has a significant disadvantage - we must be certain that 
+the app is stalkerware and that the manufacturer doesn’t make anything except 
+stalkerware. In the case of smaller apps and reskinned apps, this may actually 
+be a reasonable assumption - manufacturer names are generated to fool the 
+Google Play store into thinking the app is new, not to identify a real company, 
+and are therefore unique by necessity. We note that the two apps we identify 
+only by manufacturer are made by GPSWOX and GeoZilla. GPSWOX makes 
+location-tracking apps of all kinds, some of which may be difficult to use as 
+stalkerware, but GeoZilla’s only apps are all designed to track a phone. Since 
+only two apps were identified this way, the false positive rate should be 
+investigated further.
+We identified the following generalized signatures that can be used to identify 
+most of our apps given nothing but information available on the Google Play 
+store. The second step of our analysis will be to search for these general 
+signatures in our personal phones’ traffic captures. This will give a better 
+idea of whether it is possible to use general signatures without generating a 
+prohibitive number of false positive stalkerware detections.
 
@@
 \subsection{Network Signatures}
+\label{network_signatures}
 
@@
 
-\begin{table*}
-\begin{tabular}{p{5cm}p{5cm}p{5cm}}
-	\toprule
-	Generalized Signature & Unique Apps & Total Apps \\
-	\hline
-	Domain contains “spy,” “track,” “find” & 6 & 12 \\
-	SNI contains “spy,” “track,” “find” & 6 & 6 \\
-	User-Agent contains “spy,” “track,” “find” & 1 & 3 \\
-	User-Agent contains known app name & 1 & 1 \\
-	Domain contains known app name & 3 & 4 \\
-	SNI contains known app name & 1 & 1 \\
-	SNI contains known app manufacturer & 3 & 3 \\
-	Domain contains known app manufacturer & 3 & 3 \\
-	\midrule
-\end{tabular}
-\end{table*}
-
 \section{Future Work}
@@
 even work? What would it learn that we can't?
+
+Previously, we had expressed an interest in seeing if the signatures we found 
+by hand could identify more apps without manual inspection. There are (as far 
+as we can see) two possible methods of doing this. The first is to 
+auto-generate signatures based on a list of keywords that commonly appear in 
+domains, SNIs, User-Agents, and HTTP host names for stalkerware traffic. These 
+keywords might include the names of the apps, substrings that appear in the app 
+names, and words that seem relevant to tracking apps. A more complicated method 
+would be to set up bots that can download potential spyware by searching 
+various terms on the app store like “tracker app.” The bots would have to run 
+the apps and monitor their traffic, identifying app traffic by eliminating 
+traffic from other sources. The remaining traffic would belong to the app, and 
+the domains, SNIs, user-agents, and any other available identifying features 
+could be recorded. However, the most difficult problem in this case becomes 
+determining which apps are actually stalkerware on the app store, which is 
+beyond the scope of this project.
 

### 2019-03-19 paper/main.tex
Miscellaneous changes

@@
 users of its presence mostly consisted of one app, called SpyToMobile, that was 
-provided on the Play Store under many different names.
+provided on the Play Store under many different names (see section \ref{}).
 
@@
 \section{The Stalkerware Ecosystem}
+Some spyware has a notification that the app is running, but that can be 
+disabled. Those ones don't hide their icon, but you might have to go to All 
+Apps to find it.
 \subsection{The Practice of ``Reskinning''}
 \label{reskinning}
+As previously mentioned, spyware has a high turnover rate on the Google Play 
+store, which leads to a practice we refer to as “reskinning:” a single app will 
+be posted under many names, icons, and manufacturer names. Presumably, 
+manufacturers do this because spyware gets reported frequently and taken down - 
+we have already seen one instance of a spyware app getting removed from the 
+Play store while we were examining it. Overt stalkerware which is not available 
+through Google Play has also turned out to use reskinning, for reasons we 
+haven’t yet discovered. Apps can frequently be identified as copies of each 
+other by observing their dashboards (where users view the communications and 
+locations of the target phones), download sites, and advertisements. Several 
+groups of off-store apps have nearly identical websites, in terms of 
+organization, color, fonts, placement of buttons, prices, and other factors. 
+For example, the “ILFMobile group” consists of three different companies 
+(ILFMobile, PowerLine Group, and PhoneSpector) that claim to make a total of 
+four different apps. Further investigation showed that all three companies had 
+the same physical address in addition to identical websites. Unfortunately, 
+they also had identical bugs in their payment methods, so we were unable to 
+purchase the apps and verify that their network traces were identical. We were 
+able to check the network signatures for the rest of the app groups in the list 
+below (with the exception of one app which we are still confirming). These 
+reskinned programs are potentially a boon to our investigation as the identical 
+network signatures make it more likely that one signature generalizes across 
+multiple apps.
+We have identified the following groups of applications that appear to be 
+reskinned versions of each other.
+\begin{enumerate}
+	\item \textbf{SpyToMobile group}: Employee Work Spy by Piter Cline, SMS 
+	Tracker by TheHar, Mobile Tracking by Antwat, Cell Phone Tracker by Susdel, 
+	and Texting, Chat, 
+	Phone Spy by MaxLo. All of these apps download the same program, which is 
+	called SpyToMobile. Any app from this group installed after the first 
+	states ``SpyToMobile is already installed.''
+	\item \textbf{ILFMobile group}: HighsterMobile, PhoneSpector, Auto Forward 
+	Spy, Surepoint Spy, and EasySpy. We were unable to purchase these and 
+	ensure that they have the same signatures due to a bug in their payment 
+	system that prevented us from purchasing them.
+	\item \textbf{Codero group}: HelloSpy and TheTruthSpy have identical 
+	network signatures as well as nearly identical websites.
+	Spyzie group: Spyzie and SpyMyFone also have identical network signatures 
+	as well as identical websites.
+	\item \textbf{CallSMSTracker group}: Call and Message Tracker by Remote 
+	Karath and Cell Tracker by Trackme. These apps have identical dashboards 
+	and contact the same domains.
+\end{enumerate}
+We cannot guarantee that we have identified all of the members of any 
+particular group. If we have not, it will make other members easier to 
+identify, since signatures we have already found will scale to identify more 
+apps than we had time to download and manually examine.
+
+\subsection{Competition Among Manufacturers}
+
+App manufacturers appear to be well aware of their competition. When the term 
+``hello spy'' is typed into Google Search, ads appear labeled ``Hellospy | See 
+All Phone Data Remotely | mSpy.com'' and ``HelloSpy - Free Download | \#1 Phone 
+Tracker Software\&App | spymyfone.com.'' Clicking on these leads the user to 
+the download pages for mSpy and SpyMyFone respectively, not the site for 
+HelloSpy. Based on network traces and website appearances, we do not believe 
+any of these three apps are made by the same manufacturer. Spyware groups also 
+create “review” websites that review their own products, posing as third party 
+spyware enthusiasts. For example, a member of the ILFMobile group reviews the 
+“top 5 cell phone spy apps,” all of which are ILFMobile’s own apps, on a 
+website called “bestcellphonespyapps.com.” We haven’t determined what advantage 
+spyware manufacturers derive from appearing to make more apps and competing 
+with themselves.
 
@@
 download count?
-
-Some spyware has a notification that the app is running, but that can be 
-disabled. Those ones don't hide their icon, but you might have to go to All 
-Apps to find it.
 
@@
 each other. The most notable being the group of apps stated above, and a single 
-app mentioned before called SpyTomobile. SpyTomobile is an interesting case 
+app mentioned before called SpyToMobile. SpyToMobile is an interesting case 
 because it fits the description of a generic stalkerware app so closely that it 

### 2019-03-19 paper/main.tex
edit traffic result

--- 2019-03-19 paper/main.tex
@@
 \usepackage{makecell}
+\usepackage{booktabs}
 \renewcommand\cellalign{tl}
@@
 
-PUT NOTE HERE ABOUT THE FAMILIES THAT WE DID NOT CONFIRM VIA TRAFFIC, BUT 
-INSTEAD VIA LOOKING AT THE WEBSITES!! Otherwise we're fabricating results.
+Apps be identify as reskinned by observing their websites.
+We found several groups with similar dashboards (where users view the communications and locations of the target phones), download sites, and advertisements.
+Several groups of off-store apps have nearly identical websites, in terms of organization, color, fonts, placement of buttons, prices, and other factors.
+For example, the “ILFMobile group” consists of three different companies (ILFMobile, PowerLine Group, and PhoneSpector) that claim to make a total of four different apps.
+Further investigation showed that all three companies had the same physical address in addition to identical websites.
+Unfortunately, they also had identical bugs in their payment methods, so we were unable to purchase the apps and verify that their network traces were identical.
 

### 2019-03-19 paper/main.tex
Consolidating app families section

--- 2019-03-19 paper/main.tex
@@
 they also had identical bugs in their payment methods, so we were unable to 
-purchase the apps and verify that their network traces were identical. We were 
-able to check the network signatures for the rest of the app groups in the list 
-below (with the exception of one app which we are still confirming). These 
-reskinned programs are potentially a boon to our investigation as the identical 
-network signatures make it more likely that one signature generalizes across 
-multiple apps.
-We have identified the following groups of applications that appear to be 
-reskinned versions of each other.
+purchase the apps and verify that their network traces were identical. Other 
+app sites appear to be similar to each other in other ways, 
+with many having a large panel with a darkened image background extolling the 
+features of the app above two buttons, one for a "live demo" and the other to 
+"buy now." This is somewhat circumstantial evidence - it is entirely possible 
+that these manufacturers simply chose similar web templates, or copied each 
+other's site in an attempt to undercut competition. We therefore confirmed our 
+suspicions by checking if the traffic signatures were also similar. These 
+reskinned programs are potentially a boon to 
+our investigation as the identical network signatures make it more likely that 
+one signature generalizes across multiple apps. We have identified the 
+following groups of applications that appear to be reskinned versions of each 
+other.
 \begin{enumerate}
@@
 
+\subsubsection{SpyToMobile}
+SpyToMobile is an interesting case 
+because it fits the description of a generic stalkerware app so closely that it 
+is the perfect example of spyware on the Play Store. Moreover, this single app 
+has been repackaged multiple times. We have discovered that there are at least 
+6 copies of the app on the Play store, all with different developers and 
+different names. While this is still circumstantial evidence that most 
+stalkerware often contains copies of each other, we can at least conclude that 
+our forty-five apps constitute a larger percentage than anticipated.
+
 \subsection{Competition Among Manufacturers}
@@
 create “review” websites that review their own products, posing as third party 
-spyware enthusiasts. For example, a member of the ILFMobile group reviews the 
+spyware enthusiasts. At least one blog that is supposedly run by 
+an independent party reviewed apps that coincidentally were all made by the 
+ILFMobile group\cite{noauthor_best_nodate}. This blog reviews the 
 “top 5 cell phone spy apps,” all of which are ILFMobile’s own apps, on a 
@@
 automate the signature identification process.
-
-However, some characteristics of the stalkerware apps themselves may aid us in 
-detecting them. For example, similar to malware, some groups of apps appear to 
-be repackaged versions of each other. For example, PhoneSpector, 
-HighsterMobile, AutoForward, EasySpy and Surepoint Spy all have separate 
-websites, but the appearance of each of these sites is nearly identical. Upon 
-closer inspection, although multiple companies are listed as the makers of the 
-apps (Powerline Group Corp., ILF Mobile Apps, and PhoneSpector LLC), all have 
-the same physical address listed. At least one blog that is supposedly run by 
-an independent party reviewed apps that coincidentally were all made by the 
-same company\cite{noauthor_best_nodate}. Other app sites appear to be similar 
-to each other in other ways, 
-with many having a large panel with a darkened image background extolling the 
-features of the app above two buttons, one for a "live demo" and the other to 
-"buy now." This is somewhat circumstantial evidence - it is entirely possible 
-that these manufacturers simply chose similar web templates, or copied each 
-other's site in an attempt to undercut competition. We therefore confirmed our 
-suspicions by checking if the traffic signatures were also similar. In multiple 
-cases, this was true (see section \ref{app_families}). App identification may 
-be easier to scale since multiple groups of stalkerware apps are in fact made 
-by only a few manufacturers.
 
@@
 
-\subsection{App ``Families''}
-\label{app_families}
-After our investigation on these apps, we can confirm that, at least from the 
-few that we have selected, many stalkerware apps are related in some fashion to 
-each other. The most notable being the group of apps stated above, and a single 
-app mentioned before called SpyToMobile. SpyToMobile is an interesting case 
-because it fits the description of a generic stalkerware app so closely that it 
-is the perfect example of spyware on the Play Store. Moreover, this single app 
-has been repackaged multiple times. We have discovered that there are at least 
-6 copies of the app on the Play store, all with different developers and 
-different names. While this is still circumstantial evidence that most 
-stalkerware often contains copies of each other, we can at least conclude that 
-our forty-five apps constitute a larger percentage than anticipated.
-
-PUT NOTE HERE ABOUT THE FAMILIES THAT WE DID NOT CONFIRM VIA TRAFFIC, BUT 
-INSTEAD VIA LOOKING AT THE WEBSITES!! Otherwise we're fabricating results.
-
 \section{Future Work}

### 2019-03-19 paper/main.tex
Images of desktop lookalikes

@@
 in both features and network patterns. Unlike the overt apps, however, the vast 
-majority are usually free with advertisements. These apps can be easily 
-identified and found with a few keywords such as "spy","track", "locate", or 
-"find".
+majority are usually free with advertisements.
 
@@
 stalkerware\cite{chatterjee_spyware_2018}. An 
-additional fifteen apps were included as they were recently added to the app 
-store. Apps were chosen for their diversity of purpose and the probability that 
+additional fifteen apps were included as they were recently added to the Google 
+Play store. We found these apps by searching for keywords such as 
+"spy","track", "locate", or "find". Encouragingly, IPV-related search terms 
+such as "track girlfriend" return no results on the Play store. On the other 
+hand, that did not mean stalking apps were not available on the play store, it 
+just meant that different search terms had to be used to find them. Apps were 
+chosen for their diversity of purpose and the probability that 
 they can be used as stalkerware. These apps are the most likely to be 
-downloaded when a abuser without deep technical knowledge tries to install 
+downloaded when an abuser without deep technical knowledge tries to install 
 stalkerware since they are either the first result upon searching for 
-stalkerware, or are well known spyware apps due to advertisement or other 
-reasons.
+stalkerware, or are well known spyware apps due to advertisements.
 

### 2019-03-19 paper/main.tex
Added figures

@@
 \usepackage{booktabs}
+\usepackage{caption}
+\usepackage{subcaption}
 \renewcommand\cellalign{tl}
@@
 \label{reskinning}
+
+\begin{figure*}
+	\centering
+	\begin{subfigure}{0.8\columnwidth}
+		\centering
+		\includegraphics[width=0.9\linewidth]{../images/phonespector_small.png}
+		\caption{PhoneSpector's pricing page }
+		\label{fig:phonespector}
+	\end{subfigure}%
+	\begin{subfigure}{0.8\columnwidth}
+		\centering
+		\includegraphics[width=0.9\linewidth]{../images/highstermobile_small.png}
+		\caption{Highster Mobile's pricing page}
+	\end{subfigure}
+	\caption{PhoneSpector and Highster Mobile's payment pages. Although 
+	PhoneSpector claims to be made by PhoneSpector LLC and HighsterMobile is 
+	supposedly made by the Powerline Group, further investigation proved they 
+	were the same company.}
+	\label{fig:ilfmobiles}
+\end{figure*}
+
 As previously mentioned, spyware has a high turnover rate on the Google Play 
@@
 \subsubsection{SpyToMobile}
+
+\begin{figure}
+	\centering
+	\begin{subfigure}{0.5\columnwidth}
+		\centering
+		\includegraphics[width=0.9\linewidth]{../images/CellPhoneTracker.png}
+		\caption{SpyToMobile's setup page }
+		\label{fig:sub1}
+	\end{subfigure}%
+	\begin{subfigure}{0.5\columnwidth}
+		\centering
+		\includegraphics[width=0.9\linewidth]{../images/CoupleTrackerSetup.png}
+		\caption{One of the setup pages for Couple}
+		\label{fig:sub2}
+	\end{subfigure}
+	\caption{SpyToMobile and Couple's similarities. All SpyToMobile copies have 
+	the same setup screen as \ref{fig:sub1} as well as identical signatures. 
+	Couple did not share signatures with SpyToMobile.}
+	\label{fig:spytomobile_couple}
+\end{figure}
+
 SpyToMobile is an interesting case 
@@
 is the perfect example of spyware on the Play Store. Moreover, this single app 
-has been repackaged multiple times. We have discovered that there are at least 
-6 copies of the app on the Play store, all with different developers and 
-different names. While this is still circumstantial evidence that most 
-stalkerware often contains copies of each other, we can at least conclude that 
-our forty-five apps constitute a larger percentage than anticipated.
+has been repackaged multiple times. We have discovered that there have been at 
+least six copies of the app on the Play store while our work has been ongoing, 
+all with different developers and 
+different names. We also found that the same image SpyToMobile uses in its 
+"downloading" screen is used in another app, which had no similarities among 
+its network signatures, called Couple. Figure \ref{fig:spytomobile_couple} 
+shows the similarities.
 
@@
 App manufacturers appear to be well aware of their competition. When the term 
-``hello spy'' is typed into Google Search, ads appear labeled ``Hellospy | See 
-All Phone Data Remotely | mSpy.com'' and ``HelloSpy - Free Download | \#1 Phone 
-Tracker Software\&App | spymyfone.com.'' Clicking on these leads the user to 
-the download pages for mSpy and SpyMyFone respectively, not the site for 
+``hello spy'' is typed into Google Search, ads appear captioned ``Hellospy | 
+See All Phone Data Remotely | mSpy.com'' and ``HelloSpy - Free Download | \#1 
+Phone Tracker Software\&App | spymyfone.com.'' Clicking on these leads the user 
+to the download pages for mSpy and SpyMyFone respectively, not the site for 
 HelloSpy. Based on network traces and website appearances, we do not believe 

### 2019-03-20 paper/main.tex
changed quotes

@@
 As previously mentioned, spyware has a high turnover rate on the Google Play 
-store, which leads to a practice we refer to as “reskinning:” a single app will 
+store, which leads to a practice we refer to as "reskinning:" a single app will 
 be posted under many names, icons, and manufacturer names. Presumably, 
@@
 through Google Play has also turned out to use reskinning, for reasons we 
-haven’t yet discovered. Apps can frequently be identified as copies of each 
+haven't yet discovered. Apps can frequently be identified as copies of each 
 other by observing their dashboards (where users view the communications and 
@@
 organization, color, fonts, placement of buttons, prices, and other factors. 
-For example, the “ILFMobile group” consists of three different companies 
+For example, the "ILFMobile group" consists of three different companies 
 (ILFMobile, PowerLine Group, and PhoneSpector) that claim to make a total of 
@@
 any of these three apps are made by the same manufacturer. Spyware groups also 
-create “review” websites that review their own products, posing as third party 
+create "review" websites that review their own products, posing as third party 
 spyware enthusiasts. At least one blog that is supposedly run by 
@@
 ILFMobile group\cite{noauthor_best_nodate}. This blog reviews the 
-“top 5 cell phone spy apps,” all of which are ILFMobile’s own apps, on a 
-website called “bestcellphonespyapps.com.” We haven’t determined what advantage 
+"top 5 cell phone spy apps," all of which are ILFMobile's own apps, on a 
+website called "bestcellphonespyapps.com." We haven't determined what advantage 
 spyware manufacturers derive from appearing to make more apps and competing 
@@
 allow stalkers to monitor communications, track locations, and remotely 
-activate cameras and microphones [3,4]. In Dr. Ristenpart’s work [5], they 
+activate cameras and microphones [3,4]. In Dr. Ristenpart's work [5], they 
 proposed methods for searching IPS-related apps. By Google search query 
@@
 since techniques are available to cluster malware that comes from the same 
-source code into “families.” [8]
+source code into "families." [8]
 
@@
 		\hline
-		Domain contains “spy,” “track,” “find” & 6 & 12 \\
-		SNI contains “spy,” “track,” “find” & 6 & 6 \\
-		User-Agent contains “spy,” “track,” “find” & 1 & 3 \\
+		Domain contains "spy," "track," "find" & 6 & 12 \\
+		SNI contains "spy," "track," "find" & 6 & 6 \\
+		User-Agent contains "spy," "track," "find" & 1 & 3 \\
 		User-Agent contains known app name & 1 & 1 \\
@@
 
-In the subset of apps we studied, the words “spy,” “find,” and “track” appeared 
+In the subset of apps we studied, the words "spy," "find," and "track" appeared 
 frequently in various fields of the traffic. The most common place to find them 
-was in the destination domain, which we found using Wireshark’s reverse DNS 
+was in the destination domain, which we found using Wireshark's reverse DNS 
 lookup tool. 12 of the 26 apps that we eventually found signatures for 
 contained these spyware keywords in their domains. 
-For the apps whose traffic doesn’t contain “spy,” “find,” or “track,” we will 
+For the apps whose traffic doesn't contain "spy," "find," or "track," we will 
 next check for the app name and manufacturer name or substrings of these two. 
 Using these indicators has a significant disadvantage - we must be certain that 
-the app is stalkerware and that the manufacturer doesn’t make anything except 
+the app is stalkerware and that the manufacturer doesn't make anything except 
 stalkerware. In the case of smaller apps and reskinned apps, this may actually 
@@
 location-tracking apps of all kinds, some of which may be difficult to use as 
-stalkerware, but GeoZilla’s only apps are all designed to track a phone. Since 
+stalkerware, but GeoZilla's only apps are all designed to track a phone. Since 
 only two apps were identified this way, the false positive rate should be 
@@
 store. The second step of our analysis will be to search for these general 
-signatures in our personal phones’ traffic captures. This will give a better 
+signatures in our personal phones' traffic captures. This will give a better 
 idea of whether it is possible to use general signatures without generating a 
@@
 use their own protocols. We examined the domain, SNI, User-Agent, and HTTP 
-host, for each app. The words “spy,” “find,” and “track” appeared frequently in 
+host, for each app. The words "spy," "find," and "track" appeared frequently in 
 various fields of the traffic. The most common place to find them was in the 
-destination domain, which we found using Wireshark’s reverse DNS lookup tool. 
+destination domain, which we found using Wireshark's reverse DNS lookup tool. 
 12 of the 26 apps that we eventually found signatures for contained these 
@@
 would be to set up bots that can download potential spyware by searching 
-various terms on the app store like “tracker app.” The bots would have to run 
+various terms on the app store like "tracker app." The bots would have to run 
 the apps and monitor their traffic, identifying app traffic by eliminating 

### 2019-03-21 paper/main.tex
Added the filters

@@
 \documentclass[acmtog]{acmart}
+\usepackage{listings}
 
@@
 \usepackage{subcaption}
+\usepackage{lmodern} 
+\usepackage{amsmath} 
+\usepackage{xcolor}  
+\lstset{
+	basicstyle=\ttfamily,
+	columns=fullflexible,
+	frame=single,
+	breaklines=true,
+}
 \renewcommand\cellalign{tl}
@@
 \section{Results}
-
-\subsection{Generalizing Signatures}
-
-We picked our three keywords because of xyz reasons outlined in the checkpoint
-
-\begin{table*}
-	\begin{tabular}{p{5cm}p{5cm}p{5cm}}
-		\toprule
-		Generalized Signature & Unique Apps & Total Apps \\
-		\hline
-		Domain contains "spy," "track," "find" & 6 & 12 \\
-		SNI contains "spy," "track," "find" & 6 & 6 \\
-		User-Agent contains "spy," "track," "find" & 1 & 3 \\
-		User-Agent contains known app name & 1 & 1 \\
-		Domain contains known app name & 3 & 4 \\
-		SNI contains known app name & 1 & 1 \\
-		SNI contains known app manufacturer & 3 & 3 \\
-		Domain contains known app manufacturer & 3 & 3 \\
-		\midrule
-	\end{tabular}
-\end{table*}
-
-In the subset of apps we studied, the words "spy," "find," and "track" appeared 
-frequently in various fields of the traffic. The most common place to find them 
-was in the destination domain, which we found using Wireshark's reverse DNS 
-lookup tool. 12 of the 26 apps that we eventually found signatures for 
-contained these spyware keywords in their domains. 
-For the apps whose traffic doesn't contain "spy," "find," or "track," we will 
-next check for the app name and manufacturer name or substrings of these two. 
-Using these indicators has a significant disadvantage - we must be certain that 
-the app is stalkerware and that the manufacturer doesn't make anything except 
-stalkerware. In the case of smaller apps and reskinned apps, this may actually 
-be a reasonable assumption - manufacturer names are generated to fool the 
-Google Play store into thinking the app is new, not to identify a real company, 
-and are therefore unique by necessity. We note that the two apps we identify 
-only by manufacturer are made by GPSWOX and GeoZilla. GPSWOX makes 
-location-tracking apps of all kinds, some of which may be difficult to use as 
-stalkerware, but GeoZilla's only apps are all designed to track a phone. Since 
-only two apps were identified this way, the false positive rate should be 
-investigated further.
-We identified the following generalized signatures that can be used to identify 
-most of our apps given nothing but information available on the Google Play 
-store. The second step of our analysis will be to search for these general 
-signatures in our personal phones' traffic captures. This will give a better 
-idea of whether it is possible to use general signatures without generating a 
-prohibitive number of false positive stalkerware detections.
-
 \subsection{App Traffic}
@@
 frequency than other apps.
-
-In addition to the above network captures, we also took twenty-four hours of 
-network traffic of our own phones as a baseline for false positive rates. These 
-captures also included periods of time that were deemed high risk for false 
-positives as they emulated behaviour that is most likely to be caught by our 
-signatures. Although this may not be enough to fully emulate an entire network, 
-it is enough to prove the false positive rates on any given phone.
-
 \subsection{Network Signatures}
@@
 There are many other parts of the packets that we could attempt to match signatures for, we will explain why we cannot add more to this list.
-\section{Traffic Results}
+\subsection{Traffic Results}
 
 The majority of stalkerware apps communicate though HTTP or HTTPS, while some 
-use their own protocols. We examined the domain, SNI, User-Agent, and HTTP 
-host, for each app. The words "spy," "find," and "track" appeared frequently in 
+use their own protocols, such as STUN. We examined the domain, SNI, User-Agent, and HTTP 
+host, for each app and tried to isolate some part that we believed would be unique enough to identify that traffic.
+For the majority of the apps, they have a unique domain that each app connects to, which allowed for an easy method of filtering out their traffic.
+Some were hosted on shared cloud servers such as AWS, and so do not have a unique domain.
+These, however had a phrase in user agent or in the SNI that could be used for filtering.
+
+Initially we attempted to add on our filters with an additional check for location requests, as many stalkerware apps will contain features for tracking location.
+Additionally, when connected to a network a phone may use the router to find its current location.
+Unfortunately, while we could occasionally see a external service being used, the majority of location requests were not listed in our network captures.
+That being said, our resultant domain, user agent, and SNI filters managed to achieve full coverage of all stalkerware apps.
+
+All of our filters have been collected and are listed here. These can be directly placed in Wireshark. 
+\begin{lstlisting}
+ip.host contains dedicated.codero.net 
+|| http.host contains hellospy
+|| (ip.host contains data-api.spymyfone.com && ssl.handshake.extension.data contains "my.spymyfone.com") 
+|| (ip.host contains ws.spyzie.com && ssl.handshake.extension.data contains "ws.spyzie.com") 
+|| ip.host contains data-api.spymyfone.com 
+|| ip.host contains ws.spyzie.com 
+|| ip.host contains phonedata.me 
+|| ssl.handshake.extension.data contains "phonedata.me" 
+|| ip.host contains apiv4.alter757.info 
+|| ssl.handshake.extension.data contains "thd.cc" 
+|| ip.host contains thd.cc 
+|| ip.host contains mspyonline.com 
+|| ip.host contains corexchange.com && ssl.handshake.extensions_server_name contains messages02.smstracker.com 
+|| ip.host contains life360.helpshift.com 
+|| ip.host contains antitheft.ns1.ff.avast.com 
+|| (ip.host contains production-finderapps && ssl.handshake.extensions_server_name contains "api.familysafetyproduction.com") || ip.host contains production-finderapps 
+|| ssl.handshake.extensions_server_name contains "celulocen.zendesk.com" 
+|| ip.host contains www.zoemob.com 
+|| ip.host contains unifiedlayer.com 
+|| http.host matches "callsmstracker" 
+|| ip.dst_host matches "onlinehome-server" 
+|| (ip.dst_host matches "spoc-mu(|w|e)1.norton" && http.user_agent matches "(android|ios)")
+|| ssl.handshake.extensions_server_name matches "family.norton" 
+|| (udp && ip.host contains stun.l.google.com) 
+|| http.host == relay.google.com && http.user_agent matches test 
+|| http.host matches "97.logger.mobi" 
+|| ssl.handshake.extensions_server_name matches "gpswox" 
+|| ip.dst_host matches "gpswox" 
+|| ssl.handshake.extensions_server_name matches "geozilla" 
+|| ip.dst_host matches "clients.your-server.de" 
+|| (ip.addr == 66.147.232.135 && tcp.port == 8080 && http.request.uri contains "signalr") 
+|| ip.addr == 66.147.232.135 && tcp.port == 8080 
+|| ssl.handshake.extensions_server_name matches "findmykids" 
+|| ssl.handshake.extension.data contains "findmykids"  
+||  ip.dst_host matches "(trackmyphones.com)" 
+|| http.host matches "callsmstracker" 
+|| ip.dst_host matches "onlinehome-server" 
+ \end{lstlisting}
+
+ Unfortunately while this does catch all of the stalkerware apps we have found, it does not catch most of the stalkerware apps we have not found.
+In this case, we need to generalize our results into a format that can be either catch-all or easily scalable without requiring a network capture.
+
+\subsection{Generalizing Signatures}
+
+The words "spy," "find," and "track" appeared frequently in 
 various fields of the traffic. The most common place to find them was in the 
@@
 information available on the Google Play store.
+
+\begin{table*}
+	\begin{tabular}{p{5cm}p{5cm}p{5cm}}
+		\toprule
+		Generalized Signature & Unique Apps & Total Apps \\
+		\hline
+		Domain contains "spy," "track," "find" & 6 & 12 \\
+		SNI contains "spy," "track," "find" & 6 & 6 \\
+		User-Agent contains "spy," "track," "find" & 1 & 3 \\
+		User-Agent contains known app name & 1 & 1 \\
+		Domain contains known app name & 3 & 4 \\
+		SNI contains known app name & 1 & 1 \\
+		SNI contains known app manufacturer & 3 & 3 \\
+		Domain contains known app manufacturer & 3 & 3 \\
+		\midrule
+	\end{tabular}
+\end{table*}
+
+For the apps whose traffic do not contain "spy," "find," or "track," we will 
+next check for the app name and manufacturer name or substrings of these two. 
+Using these indicators has a significant disadvantage - we must be certain that 
+the app is stalkerware and that the manufacturer doesn't make anything except 
+stalkerware. In the case of smaller apps and reskinned apps, this may actually 
+be a reasonable assumption - manufacturer names are generated to fool the 
+Google Play store into thinking the app is new, not to identify a real company, 
+and are therefore unique by necessity. We note that the two apps we identify 
+only by manufacturer are made by GPSWOX and GeoZilla. GPSWOX makes 
+location-tracking apps of all kinds, some of which may be difficult to use as 
+stalkerware, but GeoZilla's only apps are all designed to track a phone. Since 
+only two apps were identified this way, the false positive rate should be 
+investigated further.
+We identified the following generalized signatures that can be used to identify 
+most of our apps given nothing but information available on the Google Play 
+store. The second step of our analysis will be to search for these general 
+signatures in our personal phones' traffic captures. This will give a better 
+idea of whether it is possible to use general signatures without generating a 
+prohibitive number of false positive stalkerware detections.
+\begin{lstlisting}
+http.host matches "(spy|track|find|antitheft.ns1.ff.avast|zoemob|life360|family.norton|gpswox|geozilla)" 
+|| ssl.handshake.extensions_server_name matches "(spy|track|find|antitheft.ns1.ff.avast|zoemob|life360|family.norton|gpswox|geozilla)" 
+|| http.user_agent matches "(spy|track|find|antitheft.ns1.ff.avast|zoemob|life360|family.norton|gpswox|geozilla)" 
+|| ipv6.dst_host matches "(spy|track|find|antitheft.ns1.ff.avast|zoemob|life360|family.norton|gpswox|geozilla)"
+|| ip.dst_host matches "(spy|track|find|antitheft.ns1.ff.avast|zoemob|life360|family.norton|gpswox|geozilla)"  
+|| ipv6.src_host matches "(spy|track|find|antitheft.ns1.ff.avast|zoemob|life360|family.norton|gpswox|geozilla)"
+|| ip.src_host matches "(spy|track|find|antitheft.ns1.ff.avast|zoemob|life360|family.norton|gpswox|geozilla)"
+\end{lstlisting}
+
+\section{Actual Traffic Testing}
+
+In addition to the above network captures, we also took twenty-four hours of 
+network traffic of our own phones as a baseline for false positive rates. These 
+captures also included periods of time that were deemed high risk for false 
+positives as they emulated behaviour that is most likely to be caught by our 
+signatures. Although this may not be enough to fully emulate an entire network, 
+it is enough to prove the false positive rates on any given phone.
 

### 2019-03-22 paper/main.tex
Update main.tex

@@
 frequency than other apps.
+
+Where do these stalkerware apps send their traffic?
+In general, all of our apps tested connected to a third party server that aggregated the information for display in either a website or a similar app for a separate phone.
+We had anticipated that at least one app would send tracking data directly to the abuser's phone, however this was not the case in testing.
+Perhaps setting up such a connection would be too difficult for someone who initiates intimate partner violence, or simply because it is easier to collect phone data in a dedicated server and use it for other purposes as well.
+Either way, all of the apps we found connected to a specific domain that was not the abuser's phone.
+This was both good and bad news.
+While it is much easier to find network signatures for packets being sent to a single destination with its own domain name, it also means that we will not be able to find an abuser through our method.
+This would have been an interesting tangent, unfortunately it does not work.
 \subsection{Network Signatures}
@@
 All of the above signatures are able to be filtered out through a Wireshark filter or made into a rule for a Network Intrusion Detection System such as Snort.
-There are many other parts of the packets that we could attempt to match signatures for, we will explain why we cannot add more to this list.
+There are many other parts of the packets that we could attempt to match signatures for, and we will explain why we cannot add more to this list in a later section.
 \subsection{Traffic Results}
@@
 
-\section{Actual Traffic Testing}
+\section{Real world Traffic Testing}
 
@@
 it is enough to prove the false positive rates on any given phone.
+
+Using our specific signatures, our filters did not catch any packet that could be used as stalkerware.
+This is to be expected as we are very sure that there are no stalkerware apps installed on our personal phones and the filters used are quite specific to the apps that we looked at.
+Again, these filters are very specific with their requirements and does not scale when we add more apps to our study.
+However, we can confirm that stalkerware traffic is unique, and we have a filter that very accurately catches stalkerware.
 

### 2019-03-22 paper/main.tex
edit format
Abstract changes

@@
 \begin{abstract}
-Spyware is known as unwanted software that sends user state and information to 
-an external party. Often these apps are not inherently malicious to the 
-operating system and are thus difficult to detect. We explore a subset of 
-spyware that are available in the Android Play store intended for spying on 
-another person though his or her cell phone and create a new method of 
-identifying their presence through network signatures.  
+Intimate partner violence (IPV) is a pervasive problem that has been changed by 
+the advent of the digital age. The ubiquity of smartphones has made it easy 
+even for someone with no technical skills to perform surveillance of a device 
+that they have access to. In the context of IPV, abusers often have access to 
+the devices of their partners, and either know or can coerce the passwords to 
+those devices. With such unrestricted access, an abundance of surveillance 
+options exist, 
+whether the goal is to track location, remotely block incoming calls or 
+messages, record all communications, monitor browsing history, or lock a 
+survivor out of their accounts. For some types of information, no extra 
+software is required to gather it. For example, Facebook can reveal a user's 
+location to their friends. Another example is Apple's backup service, which can 
+make copies of text messages and call logs accessible to anyone with the iCloud 
+credentials of the phone. Other types of control that might be attractive to an 
+abuser, such as the ability to block incoming communication from certain 
+people, require software to be installed on the target device. We refer to such 
+software as ``stalkerware.'' Stalkerware is dissimilar to other forms of 
+malware because of how easily the adversary can access the target device. 
+Consequently, traditional assumptions about security do not apply to it, and 
+traditional methods of studying it are ineffective. Antivirus, which can 
+normally provide information about malware, is poor at detecting 
+stalkerware.\cite{chatterjee_spyware_2018} Network Intrusion Detection Systems 
+(IDSs) also have low detection rates. This lack of information results in many 
+unanswered questions about the use of stalkerware in the context of IPV.
+
+This work takes a step towards answering one of those questions: namely, 
+\textit{how prevalent is stalkerware today?} We identify the traffic signatures 
+of 24 stalkerware apps, with the goal of being able to identify it from a 
+network operator's vantage point. We show that our signatures identify 
+stalkerware with few false positives. Additionally, we present a simple method 
+of generalizing the signatures we identify, and show that our generalized 
+signatures also give few false positives. We also show that peculiarities of 
+the stalkerware ecosystem may aid researchers in detecting it, and in 
+generalizing specific network signatures to apps that have not been manually 
+identified. The ethical and bureaucratic issues inherent in doing a large-scale 
+measurement study on real traffic prevented us from using our signatures to 
+estimate how much stalkerware exists in the wild. However, we present a plan 
+for how we could move forward. 
 \end{abstract}
@@
 \section{Introduction}
-In a world where technology now pervades every aspect of our lives, some 
-aspects of our relationships with intimate partners have changed too. 
-Specifically, when these relationships become abusive, there are more options 
+One in four women and one in six men will be subject to some sort of intimate 
+partner abuse during their lifetimes, where ``intimate partner abuse'' can 
+include physical, emotional, or sexual abuse, as well as stalking or rape. In a 
+world where technology now pervades every aspect of our lives, some 
+aspects of IPV have recently changed too. Specifically, there are more options 
 available to the abuser for attempting to retain control over their partner. 

### 2019-03-22 paper/main.tex
Moved filters to appendix

@@
 	network signatures as well as nearly identical websites.
-	Spyzie group: Spyzie and SpyMyFone also have identical network signatures 
-	as well as identical websites.
+	\item \textbf{Spyzie group}: Spyzie and SpyMyFone also have identical network signatures 
+	as well as similar websites.
 	\item \textbf{CallSMSTracker group}: Call and Message Tracker by Remote 
@@
 
-All of our filters have been collected and are listed here. These can be directly placed in Wireshark. 
-\begin{lstlisting}
-ip.host contains dedicated.codero.net 
-|| http.host contains hellospy
-|| (ip.host contains data-api.spymyfone.com && ssl.handshake.extension.data contains "my.spymyfone.com") 
-|| (ip.host contains ws.spyzie.com && ssl.handshake.extension.data contains "ws.spyzie.com") 
-|| ip.host contains data-api.spymyfone.com 
-|| ip.host contains ws.spyzie.com 
-|| ip.host contains phonedata.me 
-|| ssl.handshake.extension.data contains "phonedata.me" 
-|| ip.host contains apiv4.alter757.info 
-|| ssl.handshake.extension.data contains "thd.cc" 
-|| ip.host contains thd.cc 
-|| ip.host contains mspyonline.com 
-|| ip.host contains corexchange.com && ssl.handshake.extensions_server_name contains messages02.smstracker.com 
-|| ip.host contains life360.helpshift.com 
-|| ip.host contains antitheft.ns1.ff.avast.com 
-|| (ip.host contains production-finderapps && ssl.handshake.extensions_server_name contains "api.familysafetyproduction.com") || ip.host contains production-finderapps 
-|| ssl.handshake.extensions_server_name contains "celulocen.zendesk.com" 
-|| ip.host contains www.zoemob.com 
-|| ip.host contains unifiedlayer.com 
-|| http.host matches "callsmstracker" 
-|| ip.dst_host matches "onlinehome-server" 
-|| (ip.dst_host matches "spoc-mu(|w|e)1.norton" && http.user_agent matches "(android|ios)")
-|| ssl.handshake.extensions_server_name matches "family.norton" 
-|| (udp && ip.host contains stun.l.google.com) 
-|| http.host == relay.google.com && http.user_agent matches test 
-|| http.host matches "97.logger.mobi" 
-|| ssl.handshake.extensions_server_name matches "gpswox" 
-|| ip.dst_host matches "gpswox" 
-|| ssl.handshake.extensions_server_name matches "geozilla" 
-|| ip.dst_host matches "clients.your-server.de" 
-|| (ip.addr == 66.147.232.135 && tcp.port == 8080 && http.request.uri contains "signalr") 
-|| ip.addr == 66.147.232.135 && tcp.port == 8080 
-|| ssl.handshake.extensions_server_name matches "findmykids" 
-|| ssl.handshake.extension.data contains "findmykids"  
-||  ip.dst_host matches "(trackmyphones.com)" 
-|| http.host matches "callsmstracker" 
-|| ip.dst_host matches "onlinehome-server" 
- \end{lstlisting}
-
  Unfortunately while this does catch all of the stalkerware apps we have found, it does not catch most of the stalkerware apps we have not found.
@@
 prohibitive number of false positive stalkerware detections.
-\begin{lstlisting}
-http.host matches "(spy|track|find|antitheft.ns1.ff.avast|zoemob|life360|family.norton|gpswox|geozilla)" 
-|| ssl.handshake.extensions_server_name matches "(spy|track|find|antitheft.ns1.ff.avast|zoemob|life360|family.norton|gpswox|geozilla)" 
-|| http.user_agent matches "(spy|track|find|antitheft.ns1.ff.avast|zoemob|life360|family.norton|gpswox|geozilla)" 
-|| ipv6.dst_host matches "(spy|track|find|antitheft.ns1.ff.avast|zoemob|life360|family.norton|gpswox|geozilla)"
-|| ip.dst_host matches "(spy|track|find|antitheft.ns1.ff.avast|zoemob|life360|family.norton|gpswox|geozilla)"  
-|| ipv6.src_host matches "(spy|track|find|antitheft.ns1.ff.avast|zoemob|life360|family.norton|gpswox|geozilla)"
-|| ip.src_host matches "(spy|track|find|antitheft.ns1.ff.avast|zoemob|life360|family.norton|gpswox|geozilla)"
-\end{lstlisting}
 
@@
 
+\section{Wireshark Display Filters for Specific Signatures}
+\begin{lstlisting}
+ip.host contains dedicated.codero.net 
+|| http.host contains hellospy
+|| (ip.host contains data-api.spymyfone.com && ssl.handshake.extension.data 
+contains "my.spymyfone.com") 
+|| (ip.host contains ws.spyzie.com && ssl.handshake.extension.data contains 
+"ws.spyzie.com") 
+|| ip.host contains data-api.spymyfone.com 
+|| ip.host contains ws.spyzie.com 
+|| ip.host contains phonedata.me 
+|| ssl.handshake.extension.data contains "phonedata.me" 
+|| ip.host contains apiv4.alter757.info 
+|| ssl.handshake.extension.data contains "thd.cc" 
+|| ip.host contains thd.cc 
+|| ip.host contains mspyonline.com 
+|| ip.host contains corexchange.com && ssl.handshake.extensions_server_name 
+contains messages02.smstracker.com 
+|| ip.host contains life360.helpshift.com 
+|| ip.host contains antitheft.ns1.ff.avast.com 
+|| (ip.host contains production-finderapps && 
+ssl.handshake.extensions_server_name contains "api.familysafetyproduction.com") 
+|| ip.host contains production-finderapps 
+|| ssl.handshake.extensions_server_name contains "celulocen.zendesk.com" 
+|| ip.host contains www.zoemob.com 
+|| ip.host contains unifiedlayer.com 
+|| http.host matches "callsmstracker" 
+|| ip.dst_host matches "onlinehome-server" 
+|| (ip.dst_host matches "spoc-mu(|w|e)1.norton" && http.user_agent matches 
+"(android|ios)")
+|| ssl.handshake.extensions_server_name matches "family.norton" 
+|| (udp && ip.host contains stun.l.google.com) 
+|| http.host == relay.google.com && http.user_agent matches test 
+|| http.host matches "97.logger.mobi" 
+|| ssl.handshake.extensions_server_name matches "gpswox" 
+|| ip.dst_host matches "gpswox" 
+|| ssl.handshake.extensions_server_name matches "geozilla" 
+|| ip.dst_host matches "clients.your-server.de" 
+|| (ip.addr == 66.147.232.135 && tcp.port == 8080 && http.request.uri contains 
+"signalr") 
+|| ip.addr == 66.147.232.135 && tcp.port == 8080 
+|| ssl.handshake.extensions_server_name matches "findmykids" 
+|| ssl.handshake.extension.data contains "findmykids"  
+||  ip.dst_host matches "(trackmyphones.com)" 
+|| http.host matches "callsmstracker" 
+|| ip.dst_host matches "onlinehome-server" 
+\end{lstlisting}
+
+\section{General Signature Wireshark Display Filters}
+
+\begin{lstlisting}
+http.host matches 
+"(spy|track|find|antitheft.ns1.ff.avast|zoemob|life360|family.norton|gpswox|geozilla)"
+
+|| ssl.handshake.extensions_server_name matches 
+"(spy|track|find|antitheft.ns1.ff.avast|zoemob|life360|family.norton|gpswox|geozilla)"
+
+|| http.user_agent matches 
+"(spy|track|find|antitheft.ns1.ff.avast|zoemob|life360|family.norton|gpswox|geozilla)"
+
+|| ipv6.dst_host matches 
+"(spy|track|find|antitheft.ns1.ff.avast|zoemob|life360|family.norton|gpswox|geozilla)"
+|| ip.dst_host matches 
+"(spy|track|find|antitheft.ns1.ff.avast|zoemob|life360|family.norton|gpswox|geozilla)"
+
+|| ipv6.src_host matches 
+"(spy|track|find|antitheft.ns1.ff.avast|zoemob|life360|family.norton|gpswox|geozilla)"
+|| ip.src_host matches 
+"(spy|track|find|antitheft.ns1.ff.avast|zoemob|life360|family.norton|gpswox|geozilla)"
+\end{lstlisting}
+
 \end{table*}

### 2019-03-22 paper/main.tex
Update main.tex
fixes to charts

@@
 \appendix
+\clearpage
+\begin{table*}
 
 	\section{Apps and Signatures}
-\begin{table*}
 \begin{tabular}{p{5cm}p{5cm}p{5cm}}
@@
 
-	Mobile Surveillance and Security
-	by Trackview & \makecell{HTTP req:\\ "GET /create\_session HTTP/1.1"\\ User agent:test \\Host:relay.google.com\\
-	Domains: relay.l.google.com,\\ stun.l.google.com} & Uses STUN protocol \\
-
 \end{tabular}
@@
 	\midrule
+		Mobile Surveillance and Security
+	by Trackview & \makecell{HTTP req:\\ "GET /create\_session HTTP/1.1"\\ User agent:test \\Host:relay.google.com\\
+		Domains: relay.l.google.com,\\ stun.l.google.com} & Uses STUN protocol \\
+
 	Norton Family parental control & \makecell{domain: spoc-muw1.norton.com,\\spoc-mue1.norton.com\\
@@
 \end{tabular}
+
+\end{table*}
+\clearpage
 
@@
 
-\end{table*}
 \end{document}

### 2019-03-22 paper/main.tex
Update main.tex

@@
 
-Make machine learning identify stalkerware on the app store, download it, 
-profile it. Then train more ML to pick out the malicious signatures? Would that 
-even work? What would it learn that we can't?
+In the future, we would like to automate our process.
+Ideally we would like to use machine learning to produce signatures for apps we have deemed stalkerware and any of it's copies.
+Moreover, when we have enough signatures to comprise a training and validation set, we can apply machine learning to fuse these signatures into a compact filter.
+This would likely be a good amount of work, but if it could be created it would make most stalkerware not in our dataset easily detectable.
 
@@
 
+Additionally, we would like to actually test our signature on real word traffic.
+We are unable to do so currently since our method currently requires a network capture, and we do not have nor are able to get consent from everyone who uses a given network router.
+Hopefully we would be able to clear away these considerations in order to find the actual false positive rate of our packet filters.
+
 \section{Conclusion}
+
+Stalkerware is a problem, in the context of both society and security.
+As a tool for partner abuse, its use needs to be prevented before it can cause physical or mental harm, otherwise people cannot trust cell phones for their safety.
+As a software, current methods are unable to detect stalkerware on any given phone, the method of installation also exposes a security vulnerability that can be exploited for other purposes.
+In this paper, we have created a method that uses the intrinsic requirement of stalkerware, network communication, to detect it's presence on any device we can link to an IP address.
+This novel method is able to distinguish stalkerware traffic despite its relative simplicity.
+
+Overall, we find that our method provides a much higher chance of detection than current antivirus software or IDS.
+We believe that this method can be expanded upon to be either more accurate or more inclusive.
+This method does have issues that prevent it from actual deployment, however it provides a good step forward in detecting stalkerware.
 
@@
 
-	SpyMyFone & \makecell{HTTP 101 Switching Protocols response\\
+	SpyMyFone & \makecell{HTTP 101 Switching Protocols\\ response\\
 	Domain: data-api.spymyfone.com\\SNI my.spymyfone.com.\\
@@
 	Call and Message Tracker -Remote karanth & \makecell{SNI=www.callsmstracker.com
-	\\Domain contains onlinehome-server.com} & Similar to Cell Tracker, but uses HTTPS instead of HTTP \\
+	\\Domain contains onlinehome-server} & Similar to Cell Tracker, but uses HTTPS instead of HTTP \\
 

### 2019-03-22 paper/main.tex
Intro

--- 2019-03-22 paper/main.tex
@@
 \section{Introduction}
-One in four women and one in six men will be subject to some sort of intimate 
+Intimate partner violence, or IPV, is a pervasive problem in the United States 
+and elsewhere. One in four women and one in six men will be subject to some 
+sort of intimate 
 partner abuse during their lifetimes, where ``intimate partner abuse'' can 
@@
 world where technology now pervades every aspect of our lives, some 
-aspects of IPV have recently changed too. Specifically, there are more options 
-available to the abuser for attempting to retain control over their partner. 
-One of these options is the ability to install monitoring software on their 
-partner's phone or computer to record their online activity, communications, 
-and location. We refer to such software as ``stalkerware.''
+aspects of IPV have changed too. Technology can now be abused in a variety of 
+ways that harm survivors of IPV. Previous work \cite{ristenpart_ucsd_talk} has 
+classified these into four categories of attacks: ownership-based, account or 
+device compromise, harmful messages or posts, and exposure of private 
+information. Ownership-based attacks are possible when the abuser owns the 
+device used by the victim or the victim's children. They are then capable 
+of installing software on it that can remotely destroy the device or prevent or 
+monitor access and usage. Attacks based on account or device compromise are 
+possible when the abuser does not own the device but nevertheless can guess 
+passwords or compel the victim to reveal them, or has access to the unlocked 
+device, or can remotely ``hack'' it using knowledge of security questions or 
+passwords. Some examples of a ``harmful message'' attack include messaging the 
+victim from a spoofed account, messaging the victim's family or friends, or 
+impersonating the victim using their own accounts. Finally, attacks that expose 
+private information can involve ``revenge pornography,'' revealing an HIV 
+status, creating fake profiles offering sexual services, and blackmail. While 
+some of these options (such as tracking a victim's location) are available to 
+an abuser without installing any extra software on the phone, others are not. 
+We refer to monitoring software that can record online activity, 
+communications, and location, or remotely tamper with the device, as 
+``stalkerware.''
 
@@
 		\centering
-		\includegraphics[width=0.9\linewidth]{../images/CoupleTrackerSetup.png}
-		\caption{One of the setup pages for Couple}
+		\includegraphics[width=0.9\linewidth]{../images/Couple_like_spy2mobile.png}
+		\caption{A setup page for Couple}
 		\label{fig:sub2}
@@
 \end{tabular}
+\end{table*}
 
@@
 \end{lstlisting}
-
 \section{General Signature Wireshark Display Filters}

### 2019-03-22 paper/main.tex
Update main.tex

--- 2019-03-22 paper/main.tex
@@
 users of its presence mostly consisted of one app, called SpyToMobile, that was 
-provided on the Play Store under many different names (see section \ref{}).
+provided on the Play Store under many different names (see section \ref{subsec:The Practice of ``Reskinning''}).
 
@@
 This would have been an interesting tangent, unfortunately it does not work.
+\begin{table*}
+	\begin{tabular}{p{5cm}p{5cm}p{5cm}}
+		\toprule
+		Generalized Signature & Unique Apps & Total Apps \\
+		\hline
+		Domain contains "spy," "track," "find" & 6 & 12 \\
+		SNI contains "spy," "track," "find" & 6 & 6 \\
+		User-Agent contains "spy," "track," "find" & 1 & 3 \\
+		User-Agent contains known app name & 1 & 1 \\
+		Domain contains known app name & 3 & 4 \\
+		SNI contains known app name & 1 & 1 \\
+		SNI contains known app manufacturer & 3 & 3 \\
+		Domain contains known app manufacturer & 3 & 3 \\
+		\midrule
+	\end{tabular}
+\end{table*}
 \subsection{Network Signatures}
@@
 There are many other parts of the packets that we could attempt to match signatures for, and we will explain why we cannot add more to this list in a later section.
+
 \subsection{Traffic Results}
@@
 
-\begin{table*}
-	\begin{tabular}{p{5cm}p{5cm}p{5cm}}
-		\toprule
-		Generalized Signature & Unique Apps & Total Apps \\
-		\hline
-		Domain contains "spy," "track," "find" & 6 & 12 \\
-		SNI contains "spy," "track," "find" & 6 & 6 \\
-		User-Agent contains "spy," "track," "find" & 1 & 3 \\
-		User-Agent contains known app name & 1 & 1 \\
-		Domain contains known app name & 3 & 4 \\
-		SNI contains known app name & 1 & 1 \\
-		SNI contains known app manufacturer & 3 & 3 \\
-		Domain contains known app manufacturer & 3 & 3 \\
-		\midrule
-	\end{tabular}
-\end{table*}
-
 For the apps whose traffic do not contain "spy," "find," or "track," we will 
@@
 captures also included periods of time that were deemed high risk for false 
-positives as they emulated behaviour that is most likely to be caught by our 
+positives as they emulated behavior that is most likely to be caught by our 
 signatures. Although this may not be enough to fully emulate an entire network, 
@@
 However, we can confirm that stalkerware traffic is unique, and we have a filter that very accurately catches stalkerware.
+
+Using the generic filters, we unfortunately wrongly caught 2 TCP streams and 3 domains out of our total of 2869 streams and 1756 domains in our self network capture.
+In addition, these filters will only catch 21 out of the 24 apps that comprise the specific filter.
+This is an issue as it does infer that our generic filters are too generic.
+Upon looking at the specified domains, we see that these are most likely adware services that track user browsing data.
+Although there is a possibility that these can be considered malicious enough to add to our results, these are not stalkerware and as such count towards our false positive rate.
+Also while the percent of false positives is quite low, if we were to deploy this filter in an actual router, it would undoubtedly collect far more domains than we should be catching.
+
+While looking at domains and TCP streams gets a good sense of how our filters work in a router, ideally we would also want to see how many apps we misclassify using our generic method.
+This is because our study is based on stalkerware in phones, and we make no assumption that stalkerware is only on cellular devices.
+Since we currently cannot connect each domain or TCP stream with a single app without identifying and tracking the traffic for all of our own apps, we make the assumption that each app will connect to only one domain, with the exception of the web browser.
+Using this assumption, we see that none of the apps on our phones are caught by our filter.
+Moreover, even apps meant for tracking buses do not get caught by the filter, despite the obvious connection that one could make.
 

### 2019-03-22 paper/main.tex
Stalkerware ecosystem updates

--- 2019-03-22 paper/main.tex
@@
 Stalkerware is not as widely studied as other types of malware, and much less 
-information is available regarding it. Although it is superficially 
-similar to other types of malware, there exist a few key differences. First, 
-stalkerware is meant to be installed 
-deliberately, by someone with physical access to the device that is to be 
-monitored. In the context of intimate partner abuse, this presents an enormous 
-threat. An abuser will often know or be able to coerce passwords to the device 
-from the victim, making traditional defense measures irrelevant. This is one 
-example of how traditional assumptions about security often do not apply in the 
-context of IPV (intimate partner violence). Second, the 
+information about it is available. There are a few key differences between it 
+and other forms of malware. First, stalkerware is meant to be installed 
+by someone with physical access to the target device, not remotely by 
+exploiting vulnerabilities. In the 
+context of intimate partner abuse, this presents an enormous 
+threat, given how frequently the abuser has unfettered access to the target 
+phone. Second, the 
 threat model used by malware developers includes sophisticated antivirus and 
@@
 their presence on the target device, but malware is much more likely to 
-attempt to obfuscate its network traffic. Stalkerware does not: it does not 
+attempt to obfuscate its network traffic to thwart these adversaries. 
+Stalkerware does not: it does not 
 need to. Most antivirus does not detect apps capable of monitoring a target as 
@@
 opportunity to glean information about stalkerware that is not available in the 
-study of other forms of malware. Third, stalkerware falls 
+study of other forms of malware. At the same time, it limits a researcher's 
+ability to use information collected by antivirus as a source of information 
+about stalkerware. Third, stalkerware falls 
 for the most part into two categories: apps that are explicitly advertised for 
@@
 ``reskinning'' itself (see section \ref{reskinning}).  
-We selected several of these to test. All of these apps brand themselves as 
-spyware and advertise that their products are undetectable on the target phone, 
-despite also having disclaimers in small text that their software should not be 
-used for any illegal activity. Some use language that appears designed to 
-appeal to abusers. For example, underneath one promotional 
+We selected several of overt apps to test. All of these apps brand themselves 
+as spyware and advertise that their products are undetectable on the target 
+phone, despite also having disclaimers in small text that their software should 
+not be used for any illegal activity. Some use language that appears designed 
+to appeal to abusers. For example, underneath one promotional 
 video, the app TheOneSpy has the disclaimer: ``Note for this video: Don't 
 confuse with the world `Loved Ones' as spouse or Girl friends! Word Loved ones 
-has used for kids and teens.'' Many of these apps also refer to the tracked 
-phone as the ``target'' phone, and advertise that once installed, the app is in 
-``stealth mode,'' meaning completely undetectable. None of these required 
-rooting the phone. When installed, they ask for all the permissions they 
-require, including device administrator privileges. They are capable of 
+has used for kids and teens.''\cite{noauthor_theonespy_2013} All of these apps 
+advertise that once they are installed, they are in ``stealth mode'' and are 
+completely undetectable. This is not entirely the case - they appear in the 
+list of all applications, but take care to name themselves something innocuous 
+such as ``Data Backup'' or ``System Service.'' None of the overt apps that we 
+examined required rooting the phone. When installed, they ask for all the 
+permissions they 
+require, including device administrator privileges. They are then capable of 
 blocking incoming calls, recording messages that have been deleted, recording 
@@
 
-Other apps were overt spyware, but nevertheless available from the Play Store. 
-They fell into two categories: spyware that reskinned itself to appear to be 
-many different apps, and apps designed for parents to keep track of children 
-(or in one case, for adult children to track elderly parents.) For the most 
-part, this latter category was offered by antivirus companies such as Avast and 
-Norton. These apps offered 
+Other apps were explicitly intended as spyware, but nevertheless available from 
+the Play Store. They fell into two categories: spyware that reskinned itself to 
+appear to be many different apps, and apps designed for parents to keep track 
+of children (or in one case, for adult children to track elderly parents.) For 
+the most part, this latter category was offered by antivirus companies such as 
+Avast and Norton. These apps offered 
 multiple features, such as call screening, blocking Google search results, 
@@
 hide their app icons and generally make an effort to notify the user that the 
-monitoring app is installed on their phone. The spyware that did not notify 
-users of its presence mostly consisted of one app, called SpyToMobile, that was 
-provided on the Play Store under many different names (see section \ref{}).
+monitoring app is installed on their phone. The spyware that we found on the 
+Google Play store that did \textit{not} notify users of its presence consisted 
+of one app, which we call SpyToMobile after the title on its loading screen, 
+that was provided on the Play Store under many different names (see section 
+\ref{reskinning}).
 
 We also identified many apps that were designed to track location or text 
-messages, but were less comprehensive than the overt, off-store spyware. They 
+messages, but were less comprehensive than the overt spyware. They 
 track one feature each instead of tracking location, communication, and 
 browsing history all at once. For the most part, these apps were free and 
-available on the Google Play Store. Most of these were designed to keep track 
-of the locations of the users' friends.
+available on the Google Play Store. Most of them were designed to keep track 
+of the locations of the users' friends. They tended to be ineffective - nearly 
+all of the apps we found that did not work fell into this category. Most of 
+these apps were unable or unwilling to hide their icons, and some provide an 
+explicit notification that the app is in use, although this notification can be 
+easily disabled in the Android notification settings.
 
 \section{The Stalkerware Ecosystem}
-Some spyware has a notification that the app is running, but that can be 
-disabled. Those ones don't hide their icon, but you might have to go to All 
-Apps to find it.
+
+We noted several interesting characteristics of the stalkerware ecosystem, some 
+of which are beneficial to researchers attempting to identify stalkerware.
+
 \subsection{The Practice of ``Reskinning''}
@@
 
-Somewhere: put a note about the weird thing where the paid apps try to make you 
-download stuff again. Maybe it's just us? Maybe they're trying to boost 
-download count?
+\subsection{Does Stalkerware Download Other Malware?}
+
+Most free stalkerware appears to exist to serve advertisements. We only saw one 
+instance of an app that came packaged with other malware, which in this case 
+was a cryptominer for a cryptocurrency called Kin Coin.
+
+We also observe a strange phenomenon among at least two of the paid, overt 
+spyware apps. Both claimed that they had stopped working after two or three 
+days even though they still appeared to be updating, and asked the user to 
+click on a link to check if the app was still active. In one case, the URL of 
+this link appeared to indicate that it would always claim the app had stopped 
+working. The site would then request that the user re-download the app. We were 
+confused as to why these apps would do this. 
+The version of the app that was downloaded the second time appeared to be the 
+same as the version downloaded first, and if the manufacturer wanted to 
+download malware onto the phone, they could just do so with the first 
+download. Nevertheless, our strongest explanation for this behavior is still 
+that the false warnings were intended to convince users to download malware. We 
+leave the task of determining if this was truly the case to future work.
 
@@
 
-The other category for stalkerware encompasses a large range of quality. Many 
-apps advertised as stalkerware have absolutely no functionality other than 
-advertisement of other apps. The few that are functional are often simplistic 
-in both features and network patterns. Unlike the overt apps, however, the vast 
-majority are usually free with advertisements.
+Free stalkerware apps vary widely in quality. Many simply don't work, or claim 
+for some reason that they will only begin to work when the SIM card of the 
+phone is replaced. Multiple apps that claim to track location instead just 
+return the location associated with the phone's area code. A pair of others 
+appeared to guess randomly - one reported that a device in San Diego was in 
+Fawn Creek, Kansas, and another reported the same device was in Detroit, 
+Michegan. Another common glitch was for spyware that records texts to only 
+record one participant's side of the conversation. Their main purpose seems to 
+be to serve 
+advertisements - we did not 
+catch any of the non-functional apps contacting domains associated with malware 
+(except when the app itself was marked as malware).
 
@@
 		\midrule
-	HelloSpy & \makecell{HTTP Post to\\ <numbers>.dedicated.codero.net} & Same as TheTruthSpy HTTP \\
+		HelloSpy & \makecell{HTTP Post to\\ <numbers>.dedicated.codero.net} & 
+		Same as TheTruthSpy HTTP \\
 
-	TheTruthSpy & \makecell{HTTP Post to\\ <numbers>.dedicated.codero.net\\ User agent has hellospy in it} & Same as HelloSpy HTTP \\
+		TheTruthSpy & \makecell{HTTP Post to\\ <numbers>.dedicated.codero.net\\ 
+		User agent has hellospy in it} & Same as HelloSpy HTTP \\
 
@@
 			Domains: app-api.phonedata.me\\ws.phonedata.me\\
-	SNI with unknown domain:\\ app-api.phonedata.me} & Uses WebSocket protocol and HTTP with User agent=aliyun-sdk-android/2.3.0/Dalvik/2.1.0 (Linux; U; Android 7.1.2; Nexus 5X Build/NJH47B \\
+			SNI with unknown domain:\\ app-api.phonedata.me} & Uses WebSocket 
+			protocol and HTTP with User 
+			agent=aliyun-sdk-android/2.3.0/Dalvik/2.1.0 (Linux; U; Android 
+			7.1.2; Nexus 5X Build/NJH47B \\
 
-	Spyzie & \makecell{The same as SpyMyFone.\\ We are sure that SpyMyPhone\\ talks to spyzie.com} & Same as SpyMyFone \\
+		Spyzie & \makecell{The same as SpyMyFone.\\ We are sure that 
+		SpyMyPhone\\ talks to spyzie.com} & Same as SpyMyFone \\
 
-	iSpyoo & probably same signatures as HelloSpy and TheTruthSpy given identical websites, but apk is broken & Nonfunctional \\
+		iSpyoo & probably same signatures as HelloSpy and TheTruthSpy given 
+		identical websites, but apk is broken & Nonfunctional \\
 
@@
 
-	SMS Tracker (TheHar) & \makecell{Domain:uploads.spy2mobile.com\\ Domain contains sap4mobile} & spytomobile group (does NOT use HTTPS) \\
+		SMS Tracker (TheHar) & \makecell{Domain:uploads.spy2mobile.com\\ Domain 
+		contains sap4mobile} & spytomobile group (does NOT use HTTPS) \\
 
-	SMS Tracker TM & \makecell{Domain:cust-198-154-111-218.\\corexchange.com \\ SNI:messages02.smstracker.com} & Only tracks text. HTTPS \\
+		SMS Tracker TM & 
+		\makecell{Domain:cust-198-154-111-218.\\corexchange.com \\ 
+		SNI:messages02.smstracker.com} & Only tracks text. HTTPS \\
 
-	Find My Friends & Domain:production-finderapps-lb-1188906093.us-east-1.elb.amazonaws.com & HTTPS\\
+		Find My Friends & 
+		Domain:production-finderapps-lb-1188906093.us-east-1.elb.amazonaws.com 
+		& HTTPS\\
 
-	Avast Anti-Theft & domain:Antitheft.ns1.ff.avast.com& HTTPS. High packet counts\\
+		Avast Anti-Theft & domain:Antitheft.ns1.ff.avast.com& HTTPS. High 
+		packet counts\\
 
-	Family Locator by ZoeMob & SNIs: celulocen.zendesk.com, api.familysafetyproduction.com
+		Family Locator by ZoeMob & SNIs: celulocen.zendesk.com, 
+		api.familysafetyproduction.com
 		Domains: proxy.vip.pod5.iad1.zdsys.com, www.zoemob.com & same as Life360
@@
 
-	Couple Tracker -Mobile monitor & 162-144-96-67.unifiedlayer.com & HTTPS \\
+		Couple Tracker -Mobile monitor & 162-144-96-67.unifiedlayer.com & HTTPS 
+		\\
 
-	Call and Message Tracker -Remote karanth & \makecell{SNI=www.callsmstracker.com
-	\\Domain contains onlinehome-server} & Similar to Cell Tracker, but uses HTTPS instead of HTTP \\
+		Call and Message Tracker -Remote karanth & 
+		\makecell{SNI=www.callsmstracker.com
+			\\Domain contains onlinehome-server} & Similar to Cell Tracker, but 
+			uses HTTPS instead of HTTP \\
 
@@
 		Mobile Surveillance and Security
-	by Trackview & \makecell{HTTP req:\\ "GET /create\_session HTTP/1.1"\\ User agent:test \\Host:relay.google.com\\
-		Domains: relay.l.google.com,\\ stun.l.google.com} & Uses STUN protocol \\
+		by Trackview & \makecell{HTTP req:\\ "GET /create\_session HTTP/1.1"\\ 
+		User agent:test \\Host:relay.google.com\\
+			Domains: relay.l.google.com,\\ stun.l.google.com} & Uses STUN 
+			protocol \\
 
-	Norton Family parental control & \makecell{domain: spoc-muw1.norton.com,\\spoc-mue1.norton.com\\
+		Norton Family parental control & \makecell{domain: 
+		spoc-muw1.norton.com,\\spoc-mue1.norton.com\\
 			User-Agent: NOF/4.9.2.12/Android/8.1.0\\
@@
 
-	Senior Safety App & \makecell{POST to \\97.logger.mobi/signalr\_v1/<stuff>\\
+		Senior Safety App & \makecell{POST to 
+		\\97.logger.mobi/signalr\_v1/<stuff>\\
 			97.logger.mobi/auth/token} & requires payment\\
@@
 		Invisible Mobile GPS Tracker by
-	GPSWOX.COM & \makecell{SNI:dn.gpswox.com\\ Domain:gpswox.\\llcspnavigatio.netdna-cdn.com} & HTTPS \\
+		GPSWOX.COM & \makecell{SNI:dn.gpswox.com\\ 
+		Domain:gpswox.\\llcspnavigatio.netdna-cdn.com} & HTTPS \\
 
-	Family GPS Locator by GeoZilla & \makecell{Domain=static.<some-ip>.\\clients.your-server.de\\
-	SNI contains geozilla w/ aws domains} & NOT HTTPS (wrong ports), but TLS \\
+		Family GPS Locator by GeoZilla & 
+		\makecell{Domain=static.<some-ip>.\\clients.your-server.de\\
+			SNI contains geozilla w/ aws domains} & NOT HTTPS (wrong ports), 
+			but TLS \\
 
-	Phone Tracker By Number/Phone Tracker Family Locator & http://66.147.232.135:8080/signalr & HTTP \\
+		Phone Tracker By Number/Phone Tracker Family Locator & 
+		http://66.147.232.135:8080/signalr & HTTP \\
 
-	Automatic Call Recorder & \makecell{Domain: http://winner-lb2-\\f918b4c7bf5ab40c.\\elb.us-east-1.amazonaws.com/ }& HTTPS \\
+		Automatic Call Recorder & \makecell{Domain: 
+		http://winner-lb2-\\f918b4c7bf5ab40c.\\elb.us-east-1.amazonaws.com/ }& 
+		HTTPS \\
 
-	Find my Kids: Child GPS-watch and phone tracker & server name api.findmykids.org & Talks to yandex.net? Russian something. 
+		Find my Kids: Child GPS-watch and phone tracker & server name 
+		api.findmykids.org & Talks to yandex.net? Russian something. 
 		HTTPS \\
@@
 			Domain cs156.adn.rhocdn.net\\ with SNI req..startappservice.com,\\
-	domain cs1112.wpc.rhocdn.net\\ with SNI info.startappservice.com} & No actual tracking functions. Sets your location to Fawn creek, KS \\
+			domain cs1112.wpc.rhocdn.net\\ with SNI info.startappservice.com} & 
+			No actual tracking functions. Sets your location to Fawn creek, KS 
+			\\
 
-	track my phone pro & Domain:trackmyphones.com & HTTPS from the website, HTTP over TLS from the app \\
+		track my phone pro & Domain:trackmyphones.com & HTTPS from the website, 
+		HTTP over TLS from the app \\
 
@@
 		Cell Tracker - Trackme & Domain:Onlinehome-server.com
-	SNI:www.callsmstracker.com & Similar to Call and Message tracker. Sends a post to a separate service. \\
+		SNI:www.callsmstracker.com & Similar to Call and Message tracker. Sends 
+		a post to a separate service. \\
 
-	Texting, Chat, Phone Spy by Maxlo & Domain:spy2mobile.com & SpyToMobile lookalike \\
+		Texting, Chat, Phone Spy by Maxlo & Domain:spy2mobile.com & SpyToMobile 
+		lookalike \\
 	\end{tabular}
-\end{table*}
 
@@
 \end{lstlisting}
+
 \section{General Signature Wireshark Display Filters}

### 2019-03-22 paper/main.tex

@@
 \begin{table*}
-
 \section{Apps and Signatures}
@@
 	\midrule
-		HelloSpy & \makecell{HTTP Post to\\ <numbers>.dedicated.codero.net} & 
-		Same as TheTruthSpy HTTP \\
+	HelloSpy & \makecell{HTTP Post to\\ <numbers>.dedicated.codero.net} & Same as TheTruthSpy HTTP \\
 
-		TheTruthSpy & \makecell{HTTP Post to\\ <numbers>.dedicated.codero.net\\ 
-		User agent has hellospy in it} & Same as HelloSpy HTTP \\
+	TheTruthSpy & \makecell{HTTP Post to\\ <numbers>.dedicated.codero.net\\ User agent has hellospy in it} & Same as HelloSpy HTTP \\
 
@@
 	Domains: app-api.phonedata.me\\ws.phonedata.me\\
-			SNI with unknown domain:\\ app-api.phonedata.me} & Uses WebSocket 
-			protocol and HTTP with User 
-			agent=aliyun-sdk-android/2.3.0/Dalvik/2.1.0 (Linux; U; Android 
-			7.1.2; Nexus 5X Build/NJH47B \\
+	SNI with unknown domain:\\ app-api.phonedata.me} & Uses WebSocket protocol and HTTP with User agent=aliyun-sdk-android/2.3.0/Dalvik/2.1.0 (Linux; U; Android 7.1.2; Nexus 5X Build/NJH47B \\
 
-		Spyzie & \makecell{The same as SpyMyFone.\\ We are sure that 
-		SpyMyPhone\\ talks to spyzie.com} & Same as SpyMyFone \\
+	Spyzie & \makecell{The same as SpyMyFone.\\ We are sure that SpyMyPhone\\ talks to spyzie.com} & Same as SpyMyFone \\
 
-		iSpyoo & probably same signatures as HelloSpy and TheTruthSpy given 
-		identical websites, but apk is broken & Nonfunctional \\
+	iSpyoo & probably same signatures as HelloSpy and TheTruthSpy given identical websites, but apk is broken & Nonfunctional \\
 
@@
 
-		SMS Tracker (TheHar) & \makecell{Domain:uploads.spy2mobile.com\\ Domain 
-		contains sap4mobile} & spytomobile group (does NOT use HTTPS) \\
+	SMS Tracker (TheHar) & \makecell{Domain:uploads.spy2mobile.com\\ Domain contains sap4mobile} & spytomobile group (does NOT use HTTPS) \\
 
-		SMS Tracker TM & 
-		\makecell{Domain:cust-198-154-111-218.\\corexchange.com \\ 
-		SNI:messages02.smstracker.com} & Only tracks text. HTTPS \\
+	SMS Tracker TM & \makecell{Domain:cust-198-154-111-218.\\corexchange.com \\ SNI:messages02.smstracker.com} & Only tracks text. HTTPS \\
 
-		Find My Friends & 
-		Domain:production-finderapps-lb-1188906093.us-east-1.elb.amazonaws.com 
-		& HTTPS\\
+	Find My Friends & Domain:production-finderapps-lb-1188906093.us-east-1.elb.amazonaws.com & HTTPS\\
 
-		Avast Anti-Theft & domain:Antitheft.ns1.ff.avast.com& HTTPS. High 
-		packet counts\\
+	Avast Anti-Theft & domain:Antitheft.ns1.ff.avast.com& HTTPS. High packet counts\\
 
-		Family Locator by ZoeMob & SNIs: celulocen.zendesk.com, 
-		api.familysafetyproduction.com
+	Family Locator by ZoeMob & SNIs: celulocen.zendesk.com, api.familysafetyproduction.com
 	Domains: proxy.vip.pod5.iad1.zdsys.com, www.zoemob.com & same as Life360
@@
 
-		Couple Tracker -Mobile monitor & 162-144-96-67.unifiedlayer.com & HTTPS 
-		\\
+	Couple Tracker -Mobile monitor & 162-144-96-67.unifiedlayer.com & HTTPS \\
 
-		Call and Message Tracker -Remote karanth & 
-		\makecell{SNI=www.callsmstracker.com
-			\\Domain contains onlinehome-server} & Similar to Cell Tracker, but 
-			uses HTTPS instead of HTTP \\
+	Call and Message Tracker -Remote karanth & \makecell{SNI=www.callsmstracker.com
+	\\Domain contains onlinehome-server} & Similar to Cell Tracker, but uses HTTPS instead of HTTP \\
 

### 2019-03-23 paper/main.tex
Read-through up to Table 1

@@
 
+\section{Related Work}
+Previous studies \cite{stories_from_survivors, burke_using_2011}, the media 
+\cite{shahani_smartphones_nodate, chatterjee_spyware_2018}, and intimate 
+partner violence (IPV) survivors \cite{ristenpart_ucsd_talk} have all reported 
+that spyware is becoming an increasingly utilized means of performing
+intimate partner surveillance (IPS). Tracking functions supported by spyware 
+allow stalkers to monitor communications, track locations, and remotely 
+activate cameras and microphones \cite{shahani_smartphones_nodate, 
+chatterjee_spyware_2018}. Chatterjee et al. propose methods for searching for 
+IPS-capable apps. By Google search query expansion and unsupervised 
+classification, they collected 9,224 apps possibly related to IPS on Google 
+play and the open Internet. They manually selected 70 apps for investigation. 
+They observed the most fundamental functions of these apps are 
+monitoring locations, communication logs and data, media contents, and phone 
+usages. They also found that existing anti-spyware tools cannot effectively 
+detect IPS-related apps \cite{chatterjee_spyware_2018}.
+Mobile apps are often identified via the User-Agent string of the HTTP request, 
+when one is available \cite{xu_identifying_2011}. With the increased use of 
+HTTPS this may not always 
+be the case, but we expect to find (based on conversations with authors of 
+previous work) that security and best coding practices are not prioritized by 
+stalkerware developers. Malware identification may be of use as well, 
+since techniques are available to cluster malware that comes from the same 
+source code into "families." \cite{hutchison_firma_2013}
+
 \section{The Stalkerware Ecosystem}
@@
 
+\begin{figure*}
+	\centering
+	\begin{subfigure}{0.8\columnwidth}
+		\centering
+		\includegraphics[width=0.9\linewidth]{../images/hellospy.png}
+		\caption{HelloSpy's dashboard (cut off at bottom)}
+		\label{fig:hellospy}
+	\end{subfigure}%
+	\begin{subfigure}{0.8\columnwidth}
+		\centering
+		\includegraphics[width=0.9\linewidth]{../images/thetruthspy.png}
+		\caption{TheTruthSpy's dashboard}
+		\label{fig:truthspy}
+	\end{subfigure}
+	\caption{HelloSpy and TheTruthSpy have remarkably similar websites. Their 
+	traffic signatures also turned out to be identical, leading us to believe 
+	they are made by the same manufacturer.}
+	\label{fig:hellospy_thetruthspy}
+\end{figure*}
+
 As previously mentioned, spyware has a high turnover rate on the Google Play 
@@
 (ILFMobile, PowerLine Group, and PhoneSpector) that claim to make a total of 
-four different apps. Further investigation showed that all three companies had 
-the same physical address in addition to identical websites. Unfortunately, 
+four different apps. Their websites, however, were remarkably similar (Figure 
+\ref{fig:ilfmobiles}). Further investigation showed that all three companies 
+had the same physical address in addition to identical websites. Unfortunately, 
 they also had identical bugs in their payment methods, so we were unable to 
-purchase the apps and verify that their network traces were identical. Other 
-app sites appear to be similar to each other in other ways, 
-with many having a large panel with a darkened image background extolling the 
-features of the app above two buttons, one for a "live demo" and the other to 
-"buy now." This is somewhat circumstantial evidence - it is entirely possible 
+purchase the apps and verify that their network traces were identical. Another 
+example of stalkerware websites that appear to be strangely similar to each 
+other in other ways is shown in Figure \ref{hellospy_thetruthspy}. This is 
+admittedly somewhat circumstantial evidence - it is entirely possible 
 that these manufacturers simply chose similar web templates, or copied each 
 other's site in an attempt to undercut competition. We therefore confirmed our 
-suspicions by checking if the traffic signatures were also similar. These 
-reskinned programs are potentially a boon to 
+suspicions by checking if the traffic signatures were also similar, and found 
+that they were. These reskinned programs are potentially a boon to 
 our investigation as the identical network signatures make it more likely that 
@@
 record one participant's side of the conversation. Their main purpose seems to 
-be to serve 
-advertisements - we did not 
+be to serve advertisements - we did not 
 catch any of the non-functional apps contacting domains associated with malware 
@@
 
-\section{Related Work}
-Previous studies [1,2], the media [3,4], and intimate partner violence (IPV) 
-survivors have all reported that spyware is becoming an increasing source of 
-intimate partner surveillance (IPS). Tracking functions supported by spyware 
-allow stalkers to monitor communications, track locations, and remotely 
-activate cameras and microphones [3,4]. In Dr. Ristenpart's work [5], they 
-proposed methods for searching IPS-related apps. By Google search query 
-expansion and unsupervised classification, they collected 9,224 apps possibly 
-related to IPS on Google play and open-web. They manually selected 70 apps for 
-investigation. They observed the most fundamental functions of these apps are 
-monitoring locations, communication logs and data, media contents, and phone 
-usages. They also found that existing anti-spyware tools cannot effectively 
-detect IPS-related apps.
-Mobile apps are often identified via the User-Agent string of the HTTP request, 
-when one is available [7]. With the increased use of HTTPS this may not always 
-be the case, but we expect to find (based on conversations with authors of 
-previous work) that security and best coding practices are not prioritized by 
-stalkerware developers. Malware identification may be of limited use as well, 
-since techniques are available to cluster malware that comes from the same 
-source code into "families." [8]
+\section{Methodology}
 
-\section{Methodology}
 \subsection{Finding Apps}
@@
 stalkerware\cite{chatterjee_spyware_2018}. An 
-additional fifteen apps were included as they were recently added to the Google 
-Play store. We found these apps by searching for keywords such as 
-"spy","track", "locate", or "find". Encouragingly, IPV-related search terms 
+additional fifteen apps were included because they were recently added to the 
+Google Play store, or to replace apps that were found not to function. We found 
+these apps simply by searching for them using keywords such as "spy" or 
+"track." Encouragingly, specifically IPV-related search terms 
 such as "track girlfriend" return no results on the Play store. On the other 
 hand, that did not mean stalking apps were not available on the play store, it 
-just meant that different search terms had to be used to find them. Apps were 
-chosen for their diversity of purpose and the probability that 
-they can be used as stalkerware. These apps are the most likely to be 
+just meant that different search terms had to be used to find them. We selected 
+a diverse set of purposes, from explicit spyware to innocuous dual-use apps. We 
+predict that the apps we chose are likely to be 
 downloaded when an abuser without deep technical knowledge tries to install 
-stalkerware since they are either the first result upon searching for 
-stalkerware, or are well known spyware apps due to advertisements.
+stalkerware, since they are either among the first results upon searching for 
+stalkerware, or are well advertised as spyware.
 
-We recognize that there are thousands of apps on the market that can be 
+We recognize that there are possibly hundreds of apps on the market that can be 
 repurposed as stalkerware. Therefore, any useful process for identifying 
@@
 starting out with. Our mere forty-five apps barely scratch the surface of the 
-ecosystem, so they certainly do not provide a representative sample. Therefore, 
+ecosystem, so they may not provide a representative sample. Therefore, 
 we did not employ any vigorous app selection methods, since we know this is 
@@
 \subsection{Experimental Setup}
-Out of the 45 apps we originally selected from Dr. Ristenpart's ML-curated list 
-of stalkerware, 36 still existed on the app store. We installed these one at a 
-time on one or both of two test phones, a Nexus 5X and a Nexus 6P.These models 
+Out of the 45 apps we searched for for, 36 still existed on the app store. We 
+installed these one at a 
+time on one or both of two test phones, a Nexus 5X and a Nexus 6P. These phones 
 were chosen simply because they were readily available. Stalkerware user 
-models  fall into two types: either an app is installed on the target phone and 
-a login to a web portal is provided for the attacker to view the results, or 
+models  fall into two types: either 
+a login to a web portal is provided for the attacker to view the data, or 
 the app comes with an ``attacker'' app and a ``target'' app, and the attacker 
@@
 of five to ten minutes is enough to detect traffic going to and from the 
-stalkerware app as long as the app's tracked functions like text or GPS are 
-altered or the tracker app or website has a manual update function. Those that 
-do not have such functionality have all been fake stalkerware apps. The network 
-captures themselves contain at least one packet that provides easy manual 
-detection of the related app.
+stalkerware app as long as the functions the app tracks like text or GPS are 
+in use or the tracker app has manual update capabilities. We then manually 
+examined the traffic, isolated that which belonged to the app, and determined 
+the signature.
 
@@
 stalkerware manufacturers have leaked victims' information in the past 
-\cite{koebler_stalkerware_2018}. We took precautions by deleting all personal 
+\cite{koebler_stalkerware_2018, franceschi-bicchierai_this_2019}. We took 
+precautions by deleting all personal 
 data that had been on the phones at the start of the project. However, we were 
@@
 such as Google's RAPPOR algorithm \cite{erlingsson_rappor:_2014} to collect 
-aggregated statistics about stalkerware use, without giving ourselves the 
+aggregated statistics about stalkerware use, while denying ourselves the 
 ability to identify any particular device that had stalkerware installed. Upon 
 further investigation before we began the project, this turned out to be 
-insufficient protection. We as a computer 
-scientists do not have the expertise required to assist victims of abusive 
-relationships or domestic violence. We chose not to take our research in this 
+insufficient protection. We do not have the expertise required to assist 
+victims of abusive 
+relationships or domestic violence. If we were to uncover evidence of 
+stalkerware, it is unclear what we should or could do with that information. We 
+chose not to take our research in this 
 direction to avoid causing any unintended harm. We limit ourselves to 
-identifying traffic signatures on apps that we installed on personal phones.
+identifying traffic signatures on apps that we installed on personal phones. We 
+leave the question of deploying our signatures to later work, once we have 
+developed partnerships with experts who can advise us.
 
@@
 \section{Results}
-\subsection{App Traffic}
 
-What causes most stalkerware to send packets? Our captures and testing show 
-that there are three main categories of updating tracker state: manual, timed, 
-and on tracked feature. Most free apps fall into the manual update method, 
-where there is a button on a website or on a phone app that will send a signal 
-packet to the stalkerware app that initializes the upload. Most paid apps also 
-include a timed auto-update feature, where an update will be sent every few 
-minutes. A very small subset of both advertised that it receives a "real time 
-notification" every time email, texts, calls, or GPS, was changed or added to. 
-Our results show that none of the stalkerware apps were able to send in real 
-time, all the apps advertised as real time simply updated at a more frequent 
-frequency than other apps.
+\subsection{Network Signatures}
+\label{network_signatures}
 
-Where do these stalkerware apps send their traffic?
-In general, all of our apps tested connected to a third party server that aggregated the information for display in either a website or a similar app for a separate phone.
-We had anticipated that at least one app would send tracking data directly to the abuser's phone, however this was not the case in testing.
-Perhaps setting up such a connection would be too difficult for someone who initiates intimate partner violence, or simply because it is easier to collect phone data in a dedicated server and use it for other purposes as well.
-Either way, all of the apps we found connected to a specific domain that was not the abuser's phone.
-This was both good and bad news.
-While it is much easier to find network signatures for packets being sent to a single destination with its own domain name, it also means that we will not be able to find an abuser through our method.
-This would have been an interesting tangent, unfortunately it does not work.
+We identified the following traffic features as candidates for network 
+signatures.
+\begin{itemize}
+	\item Application Layer
+	\begin{itemize}
+		\item HTTP
+		\begin{itemize}
+			\item Packet content
+			\item User-Agent
+			\item Presence of unique header fields 
+			\item Packet length
+			\item URI
+			\item Host Name
+		\end{itemize}
+		\item Presence of excessive number of location requests
+	\end{itemize}
+	\item Transport Layer
+	\begin{itemize}
+		\item TLS 1.2
+		\begin{itemize}
+			\item Server Name Indicator
+		\end{itemize}
+		\item TCP
+		\begin{itemize}
+			\item Ports
+		\end{itemize}
+	\end{itemize}
+	\item Internet Layer
+	\begin{itemize}
+		\item IP address
+		\item Reverse-DNS-lookup domain name
+	\end{itemize}
+	\item Other
+	\begin{itemize}
+		\item Packet frequency
+	\end{itemize}
+\end{itemize}
+
+Some of these features did not prove to be easy to use as signatures.
+For example, different types of stalkerware exhibit wide variance in how often 
+they send updates back to their servers. Some apps advertise 
+``real time'' tracking, where new texts are uploaded to the service as soon as 
+they are sent by or arrive at the phone, and location is updated as soon as the 
+phone moves. In our experiments, very few of the apps who claimed this ability 
+actually delivered on their promise. Texts were uploaded anywhere between ten 
+minutes to a day after they were sent. Some of the stalkerware dashboards 
+included a button that would update or refresh the data, but this usually did 
+not trigger traffic to be sent from the phone.
+
+Another feature we failed to identify was the presence of unusually high 
+numbers of location requests. Since phones can (if GPS is not available) get 
+information about their location by seeing which WiFi AP they are connected to, 
+we attempted to identify packets that were requesting location from the AP, but 
+were unsuccessful.
+
+All of the other features proved to be useful in identifying some subset of the 
+apps we examined.
+
+\subsection{Traffic Results}
+
+The majority of stalkerware apps communicate though HTTP or HTTPS. A minority 
+use less common protocols, such as the app that could turn a phone into a live 
+video camera remotely, which used STUN. We examined the features listed above 
+for each app and tried to isolate some subset of them that we believed would be 
+unique enough to identify that traffic. For the majority of the apps, the 
+domain provided by a reverse DNS lookup was sufficient. This supported our 
+assumption that most stalkerware does not attempt to obfuscate its traffic. 
+Even servers hosted on Amazon's AWS had unique domain names, which usually 
+consisted of some string identifying the app prepended to a string identifying 
+which AWS datacenter the app is hosted by. We found signatures for 24 out of 
+the 45 apps we examined. Of the remainder, nine were removed from the Google 
+Play store before we began the project, and twelve either didn't work as 
+stalkerware or didn't work at all.
+
+\subsection{Generalizing Signatures}
 \begin{table*}
-	\begin{tabular}{p{5cm}p{5cm}p{5cm}}
+	\begin{tabular}{p{6cm}p{4cm}p{4cm}}
 		\toprule
@@
 	\end{tabular}
+	\caption{Generalized signatures, created by identifying the similarities 
+		between specific signatures}
+	\label{tab:gen}
 \end{table*}
-\subsection{Network Signatures}
-\label{network_signatures}
-
-When the network traffic is captured and the suspicious packets are identified, the next step would be to form a Network signature that can filter out those packets.
-But what can we use that isolates stalkerware traffic from normal traffic?
-To begin with, we must look at the packet identifiers that allow us to find the suspicious packets.
-\begin{itemize}
-	\item Application Layer
-	\begin{itemize}
-		\item HTTP
-		\begin{itemize}
-			\item packet content
-			\item User agent
-		\end{itemize}
-		\item HTTP and HTTPS headers
-		\item Packet length
-		\item Domain Name
-		\item Host Name
-		\item Location Requests
-	\end{itemize}
-	\item Transport Layer
-	\begin{itemize}
-		\item TLS 1.2
-		\begin{itemize}
-			\item Server Name Indication
-		\end{itemize}
-		\item TCP
-		\begin{itemize}
-			\item Ports
-			\item Sequence number
-		\end{itemize}
-	\end{itemize}
-	\item Internet Layer
-	\begin{itemize}
-		\item IP address
-		\item IP version
-	\end{itemize}
-	\item Other
-	\begin{itemize}
-		\item Packet frequency
-	\end{itemize}
-\end{itemize}
-
-All of the above signatures are able to be filtered out through a Wireshark filter or made into a rule for a Network Intrusion Detection System such as Snort.
-There are many other parts of the packets that we could attempt to match signatures for, and we will explain why we cannot add more to this list in a later section.
-
-\subsection{Traffic Results}
-
-The majority of stalkerware apps communicate though HTTP or HTTPS, while some 
-use their own protocols, such as STUN. We examined the domain, SNI, User-Agent, and HTTP 
-host, for each app and tried to isolate some part that we believed would be unique enough to identify that traffic.
-For the majority of the apps, they have a unique domain that each app connects to, which allowed for an easy method of filtering out their traffic.
-Some were hosted on shared cloud servers such as AWS, and so do not have a unique domain.
-These, however had a phrase in user agent or in the SNI that could be used for filtering.
-
-Initially we attempted to add on our filters with an additional check for location requests, as many stalkerware apps will contain features for tracking location.
-Additionally, when connected to a network a phone may use the router to find its current location.
-Unfortunately, while we could occasionally see a external service being used, the majority of location requests were not listed in our network captures.
-That being said, our resultant domain, user agent, and SNI filters managed to achieve full coverage of all stalkerware apps.
-
- Unfortunately while this does catch all of the stalkerware apps we have found, it does not catch most of the stalkerware apps we have not found.
-In this case, we need to generalize our results into a format that can be either catch-all or easily scalable without requiring a network capture.
-
-\subsection{Generalizing Signatures}
-
-The words "spy," "find," and "track" appeared frequently in 
+Since the 24 apps that we manually identified signatures for undoubtedly 
+represent a small proportion of all of the stalkerware available, we next 
+attempted to look for patterns our signatures had in common that would allow us 
+to generalize them. To our surprise, this was relatively straightforward.  
+For example, the words "spy," "find," and "track" appeared frequently in 
 various fields of the traffic. The most common place to find them was in the 
 destination domain, which we found using Wireshark's reverse DNS lookup tool. 
-12 of the 26 apps that we eventually found signatures for contained these 
-spyware keywords in their domains. We identified the following generalized 
-signatures that can be used to identify most of our apps given nothing but 
-information available on the Google Play store.
+12 of the 24 apps that we eventually found signatures for contained these 
+spyware keywords in their domains. We therefore labeled this signature the 
+``keyword method.''
 
-For the apps whose traffic do not contain "spy," "find," or "track," we will 
-next check for the app name and manufacturer name or substrings of these two. 
+For the apps whose traffic do not contain "spy," "find," or "track," we 
+next check for the app name, the manufacturer name, or substrings of either. 
 Using these indicators has a significant disadvantage - we must be certain that 
@@
 stalkerware. In the case of smaller apps and reskinned apps, this may actually 
-be a reasonable assumption - manufacturer names are generated to fool the 
+be a reasonable assumption. Manufacturer names are generated to fool the 
 Google Play store into thinking the app is new, not to identify a real company, 
-and are therefore unique by necessity. We note that the two apps we identify 
-only by manufacturer are made by GPSWOX and GeoZilla. GPSWOX makes 
+and are therefore unique by necessity. We note that the two apps we can only 
+identify by manufacturer are made by GPSWOX and GeoZilla. GPSWOX makes 
 location-tracking apps of all kinds, some of which may be difficult to use as 
@@
 investigated further.
-We identified the following generalized signatures that can be used to identify 
-most of our apps given nothing but information available on the Google Play 
-store. The second step of our analysis will be to search for these general 
-signatures in our personal phones' traffic captures. This will give a better 
-idea of whether it is possible to use general signatures without generating a 
-prohibitive number of false positive stalkerware detections.
 
-\section{Real world Traffic Testing}
+The generalized signatures shown in Table \ref{tab:gen} can be used to identify 
+all but three (12.5\%) of our apps given nothing but information available on 
+the Google Play store. This means that if we were able to reliably identify 
+apps on the 
+Play Store than can be used as stalkerware, it would be possible to identify 
+the traffic of a large fraction of them without having to manually find their 
+signatures.
 
-In addition to the above network captures, we also took twenty-four hours of 
-network traffic of our own phones as a baseline for false positive rates. These 
+\section{Evaluation}
+
+We evaluated both specific and general signatures by taking twenty-four hours 
+of network traffic captures on our own personal phones. Our goal was to 
+determine a lower bound for our false positive rates. These 
 captures also included periods of time that were deemed high risk for false 
 positives as they emulated behavior that is most likely to be caught by our 
-signatures. Although this may not be enough to fully emulate an entire network, 
-it is enough to prove the false positive rates on any given phone.
+signatures. Given the relatively small amount of data we have to work with, our 
+results should be considered extremely conservative lower bounds on the true 
+false positive rates of our signatures. TODO: explain how we got false pos rate
 
-Using our specific signatures, our filters did not catch any packet that could be used as stalkerware.
-This is to be expected as we are very sure that there are no stalkerware apps installed on our personal phones and the filters used are quite specific to the apps that we looked at.
-Again, these filters are very specific with their requirements and does not scale when we add more apps to our study.
-However, we can confirm that stalkerware traffic is unique, and we have a filter that very accurately catches stalkerware.
+Using the specific signatures, our false positive rate was zero. This is to be 
+expected as we are very sure that there 
+are no stalkerware apps installed on our personal phones and the filters used 
+are quite specific to the apps that we looked at.
 
-Using the generic filters, we unfortunately wrongly caught 2 TCP streams and 3 domains out of our total of 2869 streams and 1756 domains in our self network capture.
-In addition, these filters will only catch 21 out of the 24 apps that comprise the specific filter.
-This is an issue as it does infer that our generic filters are too generic.
-Upon looking at the specified domains, we see that these are most likely adware services that track user browsing data.
-Although there is a possibility that these can be considered malicious enough to add to our results, these are not stalkerware and as such count towards our false positive rate.
-Also while the percent of false positives is quite low, if we were to deploy this filter in an actual router, it would undoubtedly collect far more domains than we should be catching.
+Using the generic filters, we identified two TCP streams and 3 domains out of 
+our total of 2869 streams and 1756 domains in our self network capture. In 
+addition, these filters will only catch 21 out of the 24 apps that comprise the 
+specific filter. This is an issue as it does infer that our generic filters are 
+too generic. Upon looking at the specified domains, we see that these are most 
+likely adware services that track user browsing data. Although there is a 
+possibility that these can be considered malicious enough to add to our 
+results, these are not stalkerware and as such count towards our false positive 
+rate. Also while the percent of false positives is quite low, if we were to 
+deploy this filter in an actual router, it would undoubtedly collect far more 
+domains than we should be catching.
 

### 2019-03-23 paper/main.tex
Finished run-through number 1

@@
 Google Play store into thinking the app is new, not to identify a real company, 
-and are therefore unique by necessity. We note that the two apps we can only 
-identify by manufacturer are made by GPSWOX and GeoZilla. GPSWOX makes 
+and are therefore unique by necessity. We note that the two apps whose only 
+general signature is their manufacturer are made by GPSWOX and GeoZilla. GPSWOX 
+makes 
 location-tracking apps of all kinds, some of which may be difficult to use as 
@@
 
-We evaluated both specific and general signatures by taking twenty-four hours 
+We evaluated both specific and general signatures by taking 24 hours 
 of network traffic captures on our own personal phones. Our goal was to 
 determine a lower bound for our false positive rates. These 
-captures also included periods of time that were deemed high risk for false 
-positives as they emulated behavior that is most likely to be caught by our 
-signatures. Given the relatively small amount of data we have to work with, our 
+captures also included periods of time where we attempted to trigger false 
+positives by emulating behavior that might match our 
+signatures. For example, we used the UCSD shuttle tracking app in the hopes 
+that it would get caught by the keyword method for containing the word 
+``track.'' Given the relatively small 
+amount of data we have to work with, our 
 results should be considered extremely conservative lower bounds on the true 
-false positive rates of our signatures. TODO: explain how we got false pos rate
+false positive rates of our signatures. Ideally, we would determine the false 
+positive rate by counting how many apps our method misclassifies. However, 
+separating traffic by the originating application is a nontrivial problem that 
+we were not able to solve in the time available. We settled for two 
+approximations: the number of misclassifed TCP streams and the number of 
+misclassified domains.
 
@@
 
-Using the generic filters, we identified two TCP streams and 3 domains out of 
-our total of 2869 streams and 1756 domains in our self network capture. In 
-addition, these filters will only catch 21 out of the 24 apps that comprise the 
-specific filter. This is an issue as it does infer that our generic filters are 
-too generic. Upon looking at the specified domains, we see that these are most 
-likely adware services that track user browsing data. Although there is a 
-possibility that these can be considered malicious enough to add to our 
-results, these are not stalkerware and as such count towards our false positive 
-rate. Also while the percent of false positives is quite low, if we were to 
-deploy this filter in an actual router, it would undoubtedly collect far more 
-domains than we should be catching.
-
-While looking at domains and TCP streams gets a good sense of how our filters work in a router, ideally we would also want to see how many apps we misclassify using our generic method.
-This is because our study is based on stalkerware in phones, and we make no assumption that stalkerware is only on cellular devices.
-Since we currently cannot connect each domain or TCP stream with a single app without identifying and tracking the traffic for all of our own apps, we make the assumption that each app will connect to only one domain, with the exception of the web browser.
-Using this assumption, we see that none of the apps on our phones are caught by our filter.
-Moreover, even apps meant for tracking buses do not get caught by the filter, despite the obvious connection that one could make.
+Using the general filters, we identified two TCP streams and three domains out 
+of our total of 2,869 streams (0.07\%) and 1,756 domains (0.2\%) in our 24 
+hours of personal traffic. In addition, these filters will only catch 21 out of 
+our 24 apps, making the general filetrs' false negative rate 12.5\%. The 
+misclassified domains are all advertisement services that 
+track user browsing data. While the percentage of false positives is quite low, 
+we are wary of assigning it too much significance. We predict that if we were 
+to deploy this filter in a real router, it 
+would undoubtedly collect far more domains than we did with our personal 
+traffic.
 
@@
 
-In the future, we would like to automate our process.
-Ideally we would like to use machine learning to produce signatures for apps we have deemed stalkerware and any of it's copies.
-Moreover, when we have enough signatures to comprise a training and validation set, we can apply machine learning to fuse these signatures into a compact filter.
-This would likely be a good amount of work, but if it could be created it would make most stalkerware not in our dataset easily detectable.
-
-Previously, we had expressed an interest in seeing if the signatures we found 
-by hand could identify more apps without manual inspection. There are (as far 
-as we can see) two possible methods of doing this. The first is to 
-auto-generate signatures based on a list of keywords that commonly appear in 
-domains, SNIs, User-Agents, and HTTP host names for stalkerware traffic. These 
-keywords might include the names of the apps, substrings that appear in the app 
-names, and words that seem relevant to tracking apps. A more complicated method 
+In the future, we would like to automate our signature identification process. 
+If we could acquire enough signatures to comprise a training and validation 
+set, we could determine whether machine learning could help us accurately 
+distinguish stalkerware from innocent apps. A more complicated method 
 would be to set up bots that can download potential spyware by searching 
@@
 could be recorded. However, the most difficult problem in this case becomes 
-determining which apps are actually stalkerware on the app store, which is 
-beyond the scope of this project.
+determining which apps are actually stalkerware on the app store without 
+examining their traffic first.
 
-Additionally, we would like to actually test our signature on real word traffic.
-We are unable to do so currently since our method currently requires a network capture, and we do not have nor are able to get consent from everyone who uses a given network router.
-Hopefully we would be able to clear away these considerations in order to find the actual false positive rate of our packet filters.
+Additionally, we would like to actually test our signatures on real word 
+traffic. We are unable to do so currently since our method currently requires a 
+network capture, and we do not have nor are able to get consent from everyone 
+who uses a given network router. We would like to find a way to use 
+differential privacy (such as RAPPOR \cite{erlingsson_rappor:_2014}) to ensure 
+that we can only collect aggregate statistics on 
+stalkerware usage, without identifying any device as having it, but have yet to 
+find a way to set that up.
 
@@
 
-Stalkerware is a problem, in the context of both society and security.
-As a tool for partner abuse, its use needs to be prevented before it can cause physical or mental harm, otherwise people cannot trust cell phones for their safety.
-As a software, current methods are unable to detect stalkerware on any given phone, the method of installation also exposes a security vulnerability that can be exploited for other purposes.
-In this paper, we have created a method that uses the intrinsic requirement of stalkerware, network communication, to detect it's presence on any device we can link to an IP address.
-This novel method is able to distinguish stalkerware traffic despite its relative simplicity.
-
-Overall, we find that our method provides a much higher chance of detection than current antivirus software or IDS.
-We believe that this method can be expanded upon to be either more accurate or more inclusive.
-This method does have issues that prevent it from actual deployment, however it provides a good step forward in detecting stalkerware.
+Stalkerware is a pervasive and troubling problem, in the context of both 
+society and security. As a tool for partner abuse, its use needs to be 
+prevented before it can cause physical or mental harm, otherwise people cannot 
+trust cell phones for their safety. Current methods of stalkerware detection 
+are unreliable, leading to a lack of data on their use. The context in which 
+stalkerware is used also invalidates many assumptions about computer security, 
+such as the idea that strong passwords and antivirus can keep a phone free of 
+malware. We have taken a step towards answering the question of how much 
+stalkerware is in existence by creating signatures for network traffic. This 
+novel method is able to distinguish stalkerware traffic despite 
+its relative simplicity. We also describe several findings about the 
+stalkerware ecosystem, the most interesting of which is the knowledge of how 
+many apparently unique apps are actually copies of one another. Our methods 
+can certainly be expanded upon to be either more accurate or more 
+inclusive, but they provide a good step forward in detecting stalkerware.
 

### 2019-03-23 paper/main.tex
Minor edits

@@
 messages, record all communications, monitor browsing history, or lock a 
-survivor out of their accounts. For some types of information, no extra 
-software is required to gather it. For example, Facebook can reveal a user's 
+survivor out of their accounts. No extra software is required to gather some 
+types of information. For example, Facebook can reveal a user's 
 location to their friends. Another example is Apple's backup service, which can 
@@
 \textit{how prevalent is stalkerware today?} We identify the traffic signatures 
-of 24 stalkerware apps, with the goal of being able to identify it from a 
+of 24 stalkerware apps, with the goal of being able to identify them from a 
 network operator's vantage point. We show that our signatures identify 
@@
 signatures also give few false positives. We also show that peculiarities of 
-the stalkerware ecosystem may aid researchers in detecting it, and in 
+the stalkerware ecosystem may aid researchers in detecting stalkerware, and in 
 generalizing specific network signatures to apps that have not been manually 
-identified. The ethical and bureaucratic issues inherent in doing a large-scale 
+identified. The ethical issues inherent in doing a large-scale 
 measurement study on real traffic prevented us from using our signatures to 
@@
 aspects of IPV have changed too. Technology can now be abused in a variety of 
-ways that harm survivors of IPV. Previous work \cite{ristenpart_ucsd_talk} has 
-classified these into four categories of attacks: ownership-based, account or 
-device compromise, harmful messages or posts, and exposure of private 
+ways that harm victims of IPV. Previous work \cite{ristenpart_ucsd_talk} has 
+classified these into four categories of attacks: ownership-based attacks, 
+account or device compromise, harmful messages or posts, and exposure of 
+private 
 information. Ownership-based attacks are possible when the abuser owns the 
@@
 prevention, finding lost devices, parental control of children, and employer 
-control of employees. Previous literature refers to these as "dual-use" 
-apps\cite{chatterjee_spyware_2018}. Some dual-use apps are ones that the 
+control of employees. Previous literature refers to these as ``dual-use'' 
+apps \cite{chatterjee_spyware_2018}. Some dual-use apps are ones that the 
 victim wants to keep installed, such as 
@@
 GPS. 75\% said they have worked with clients who have had their conversations 
-monitored by hidden stalkerware apps.\cite{shahani_smartphones_nodate} However, 
+monitored by hidden stalkerware apps \cite{shahani_smartphones_nodate}. 
+However, 
 this study does not report how many individual clients experienced being 
@@
 can be enumerated. We identified unique signatures in the traffic of 24 
-stalkerware apps, by examining a traffic features such as domain names, HTTP 
+stalkerware apps, by examining traffic features such as domain names, HTTP 
 header fields, protocol, and server name indicators (SNIs). For a complete 
@@
 two test phones were both Androids. Apps that appear in Google searches for 
-terms like 
-"catch a cheating spouse," use vague language that appear to be marketed 
-towards IPS, and label themselves as "spyware" became candidates that we 
-considered. Overt spyware is not generally available from the app store - it 
-must be downloaded from the manufacturer sites. It also costs much more than a 
-typical app, with monthly 
+terms like ``catch a cheating spouse,'' use vague language that appear to be 
+marketed towards IPS, and label themselves as ``spyware'' became candidates 
+that we considered. Stalkerware marketed for tracking a romantic partner is not 
+generally available from the app store - it must be downloaded from the 
+manufacturer sites. It also costs much more than a typical app, with monthly 
 subscriptions ranging from \$12 to \$70 per month. The exception is an app that 
@@
 ``reskinning'' itself (see section \ref{reskinning}).  
-We selected several of overt apps to test. All of these apps brand themselves 
+We selected several of the most overt apps to test. All of these apps brand 
+themselves 
 as spyware and advertise that their products are undetectable on the target 
@@
 monitoring app is installed on their phone. The spyware that we found on the 
-Google Play store that did \textit{not} notify users of its presence consisted 
-of one app, which we call SpyToMobile after the title on its loading screen, 
+Google Play store that did \textit{not} notify users of its presence mostly 
+consisted of copies of one app, which we call SpyToMobile after the title on 
+its loading screen, 
 that was provided on the Play Store under many different names (see section 
@@
 these apps were unable or unwilling to hide their icons, and some provide an 
-explicit notification that the app is in use, although this notification can be 
+explicit notification that the app is in use, although this notification can 
+usually be 
 easily disabled in the Android notification settings.
@@
 Previous studies \cite{stories_from_survivors, burke_using_2011}, the media 
-\cite{shahani_smartphones_nodate, chatterjee_spyware_2018}, and intimate 
-partner violence (IPV) survivors \cite{ristenpart_ucsd_talk} have all reported 
+\cite{shahani_smartphones_nodate, chatterjee_spyware_2018}, and IPV survivors 
+\cite{ristenpart_ucsd_talk} have all reported 
 that spyware is becoming an increasingly utilized means of performing
-intimate partner surveillance (IPS). Tracking functions supported by spyware 
+IPS. Tracking functions supported by spyware 
 allow stalkers to monitor communications, track locations, and remotely 
@@
 chatterjee_spyware_2018}. Chatterjee et al. propose methods for searching for 
-IPS-capable apps. By Google search query expansion and unsupervised 
-classification, they collected 9,224 apps possibly related to IPS on Google 
-play and the open Internet. They manually selected 70 apps for investigation. 
+IPS-capable apps. Using Google search query expansion and unsupervised 
+classification, they collected 9,224 apps possibly related to IPS on the Google 
+Play store and the open Internet. They manually selected 70 apps for 
+investigation. 
 They observed the most fundamental functions of these apps are 
@@
 usages. They also found that existing anti-spyware tools cannot effectively 
-detect IPS-related apps \cite{chatterjee_spyware_2018}.
-Mobile apps are often identified via the User-Agent string of the HTTP request, 
+detect IPS-related apps \cite{chatterjee_spyware_2018}. In terms of previous 
+work on app detection, mobile apps are often identified via the User-Agent 
+string of the HTTP request, 
 when one is available \cite{xu_identifying_2011}. With the increased use of 
@@
 since techniques are available to cluster malware that comes from the same 
-source code into "families." \cite{hutchison_firma_2013}
+source code into ``families'' \cite{hutchison_firma_2013}.
 
